### 2021-08-26 article/article.tex
initial commit

\documentclass[a4paper, 10 pt, conference]{ieeeconf}  % Comment this line out
\IEEEoverridecommandlockouts% This command is only
                                                          % needed if you want to
 \pdfminorversion=4                                                         % use the \thanks command
% \overrideIEEEmargins

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\input{preamble}
% \usepackage[showframe]{geometry}
\usepackage{geometry}
\usepackage{stfloats}
\geometry{
  textwidth=\columnwidth,
  top=19.1mm,
  bottom=36.7mm,
  left=19.1mm,
  right=13.1mm,
}

\title{\LARGE \bf
Detection and Mitigation of Corrupted Information in Distributed Model Predictive Control Based on Resource Allocation
}

\author{Rafael Accácio Nogueira, Romain Bourdais and Hervé Guéguen
% <-this % stops a space
\thanks{The authors are with IETR-CentraleSupélec, 35510\newline Cesson-Sévigné, Ille-et-Vilaine, France \newline {\tt\small
\{rafael-accacio.nogueira, romain.bourdais, herve.gueguen\}
@centralesupelec.fr}\newline
}%
}

\makeatletter
\hypersetup{
    bookmarks=true,         % show bookmarks bar?
    unicode=false,          % non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={\@title},    % title
    pdfauthor={\@author},     % author
    pdfsubject={Automatique},   % subject of the document
    pdfcreator={Rafael Accácio},   % creator of the document
    % pdfproducer={Producer}, % producer of the document
    pdfkeywords={keyword1, key2, key3}, % list of keywords
    pdfnewwindow=true,                  % links in new PDF window
    colorlinks=true,            % false: boxed links; true: colored links
    % colorlinks=false,            % false: boxed links; true: colored links
    linkcolor=black, % color of internal links (change box color with linkbordercolor)
    citecolor=black,          % color of links to bibliography
    filecolor=black,          % color of file links
    urlcolor=black            % color of external links
}
\makeatother

\draft%
% \final%

\makeglossaries
\begin{document}
\maketitle
% \IEEEpeerreviewmaketitle% This command is only
\thispagestyle{empty}
\pagestyle{empty}

\begin{abstract}
  In distributed predictive control structures, communication among agents is required to achieve a consensus and approach an optimal global behavior. Such negotiation mechanisms are sensitive to attacks on these exchanges.
  This paper proposes a monitoring scheme that detects and mitigates these attacks' effects in a resource allocation framework.
  The performance of the proposed method is illustrated through simulations of the temperature control of multiple rooms under power scarcity.
\end{abstract}

%===============================================================================
\section{INTRODUCTION}
Recent performance objectives require systems to be driven not in isolation but
in a coordinated way, emphasizing large systems.
These systems cover many applications, such as energy distribution systems,
traffic management in Smart City environments, coordinated control of
intelligent building systems, and many others.
Many works are built around model predictive control~\cite{CamachoBordons2007} to integrate optimality and constraints.

Furthermore, distributed model predictive control (DMPC)~\cite{MaestreEtAl2014}
techniques are a promising way to handle the optimization problem's complexity.
In these structures, there is no longer a single controller for all systems.
Instead, we use a set of local communicating controllers.
These strategies thus reduce the computing burden while increasing
confidentiality.

Many works use distributed optimization techniques, such as
Lagrangian relaxation~\cite{BourdaisEtAl2012}, Alternating Direction Method of
Multipliers (ADMM)~\cite{BoydEtAl2011}, primal
decomposition~\cite{PaulenEtAl2016}, dual decomposition~\cite{VelardeEtAl2017,VelardeEtAl2017a,PflaumEtAl2014}, and others~\cite{ChanfreutEtAl2018,Cohen1978}.
In these methods, local agents interact with a coordinator who uses an iterative process to ensure convergence towards the solution of the initial
problem.

Usually, it is assumed that all agents work in perfect cooperation.
However, when it is not the case, these uncooperative behavior have pernicious effects on the overall system, and their impact can be studied.
The cause of this disruptive behavior can be either involuntary due to hacking or malfunctioning, or voluntary, by developing selfish behavior.
Recent work has begun to explore this issue.
In the article~\cite{VelardeEtAl2017}, the authors are interested in the vulnerabilities induced when distributed predictive control is built on dual decomposition.
They analyze the impact of the deception depending on where it occurs: either in the followed references or directly in the local cost functions or coupling constraints.
The same authors propose defense strategies against these attacks, either by using secure scenarios based on reliable historical data~\cite{VelardeEtAl2017a} or by ignoring extreme values of control signals~\cite{VelardeEtAl2017}.
Then~\cite{ChanfreutEtAl2018} extends the initial work to analyze the vulnerabilities of the Jacobi-Gauss decomposition method.

Another way of dealing with these changes in behavior can be using robust distributed control principles, coupled with hierarchical identification of the attack~\cite{BraunEtAl2020}, or the introduction of probabilistic models that implement a resilient strategy if the information exchanged is outside the confidence interval~\cite{AnandutaEtAl2020}.

In this work, we analyze the exchange among agents controlled by DMPC using primal decomposition, which is perfectly adapted for agents that share resources.
More specifically, we are interested when malicious agent steers these exchanges.
By exploiting the nominal structure that characterizes the communication between the agents and the coordinator, we propose a monitoring scheme that detects an attack, and if necessary, corrects it.

The remainder of this paper is organized as follows.
First, in Section~\ref{sec:PS}, the primal decomposition-based DMPC is introduced.
In Section~\ref{sec:attack}, we discuss a model of the agents' selfish behavior that exploits the vulnerabilities of this DMPC structure.
Then, in Section~\ref{sec:mitigation}, we discuss the structure of the DMPC and how we can exploit it to construct a defense scheme to counteract the selfish agent.
At last, we present a particular mechanism to detect the agents' selfish behavior and mitigate its effects.
Moreover, in Section~\ref{sec:App_dMPC}, an application is given to illustrate and evaluate the algorithm's performance.
Finally, in Section~\ref{sec:CC}, we conclude, and we give an outlook of future works.

\section{PRELIMINARIES AND PROBLEM STATEMENT}\label{sec:PS}
\emph{Notation:} In this paper, $\|\cdot\|$ and $\|\cdot\|_{F}$ represent the $\ell_{2}$ and Frobenius norms. $\|\vec{v}\|_{Y}$ is the weighted norm, $\|Y^{1\over 2}\vec{v}\|$.
$P_{\mathsf{T}}(\cdot)$ is the Euclidean projection onto set $\mathsf{T}$.
$\otimes$ represents the Kronecker product. $\1_{m,n}$ is a ${m\times n}$ matrix filled with $1$.
$I_{c}$ is a ${c\times c}$ identity matrix.
$\pi_{v}$ denotes the number of elements in $v$.
A vector $\vec{v}_{i}$, correspond to the $i$-th agent, and these vectors can be stacked in a vector $\vec{v}$.

\subsection{Model Predictive Control}\label{ssec:MPC}
Our primary purpose is to control a system composed of $M$ subsystems using MPC\@.
The dynamics of the state ${\vec{x}_{i}(k)}$ of $i$-th agent w.r.t
input ${\vec{u}_{i}(k)}$ are described by the following linear discrete-time systems:
\begin{equation}
\begin{matrix}
  \label{eq:systems}
\vec{x}_{i}(k+1)=A_{i}\vec{x}_{i}(k) + B_{i}\vec{u}_{i}(k)
\end{matrix}
\end{equation}

The $M$ subsystems are coupled under linear input constraints.
We assume as an interesting case when these constraints prevent the subsystems from meeting the systems' needs. Consequently, the constraints will always be active, yielding the same results from equality constraints~\cite{BoydVandenberghe2004}:
\begin{equation}
  \label{eq:constraint}
  \sum^{M}_{i=1}\Gamma_{i}\vec{u}_{i}(k)=\vec{u}_{\mathrm{\max}}
\end{equation}
where $\Gamma_{i}:\R^{\pi_{\vec{u}_{i}(k)}\times \pi_{\vec{u}_{i}(k)}}$ and $\vec{u}_{\mathrm{max}}:\R^{\pi_{\vec{u}_{i}(k)}\times 1}$.

A known formulation of the MPC structure~\cite{CamachoBordons2007,VelardeEtAl2017,VelardeEtAl2017a,SimonEtAl2012,ChanfreutEtAl2018} with finite prediction horizon $N_{p}$ is the following:
\begin{problem}{Global MPC Problem.}\label{Pb:GOP}
\begin{equation*}
\begin{matrix}
\underset{\vec{u}_i(k:k+N_{p}-1|k)}{\mathrm{minimize}}&\resizebox{0.35\textwidth}{!}{$\overbrace{\sum\limits^{M}_{i=1} \overbrace{\sum_{j=1}^{N_{p}}\|\vec{v}_i(k+j|k)\|^{2}_{Q_i}+\|\vec{u}_i(k+j-1|k)\|^{2}_{R_i}}^{\textstyle J_{i}(k)}}^{\textstyle J_{G}(k)}$}\\
\mathrm{subject~ to}&~\eqref{eq:systems}\mathrm{~and~}\eqref{eq:constraint}
\left\}\small
\begin{aligned}
  &\forall i\in\{1,\dots,M\}\\
  &\forall j\in\{1,\dots,N_{p}\}
\end{aligned}\right.

\end{matrix}
\label{eq:dmpcModLOP}
\end{equation*}
with symmetric weight matrices ${Q_{i}\geq0}$, ${R_{i}>0}$. $\vec{v}_{i}(k)$ represents a control objective. It can either be ${\vec{v}_{i}(k)=\vec{w}_{i}(k)-\vec{x}_{i}(k)}$ for reference tracking, where $\vec{w}_{i}(k)$ is a state reference, or ${\vec{v}_{i}(k)=\vec{x}_{i}(k)}$ for disturbance rejection.

The optimal value of the problem~\ref{Pb:GOP}
is denoted by $J^{\star}$, and the optimal control sequences are represented by ${\vec{u}_i^{\star}(k:k+N_{p}-1|k)}$.
At each time $k$, the problem is solved, and the $\vec{u}_i^{\star}(k|k)$ are applied in each respective $i$ subsystem, following a receding horizon strategy.
\end{problem}

One can see that if the subsystems were not coupled by~\eqref{eq:constraint},  the overall system could be decomposed into $M$ parts, solvable in parallel.
Multiple decomposition methods solve this problem~\cite{BoydEtAl2011,PaulenEtAl2016,PflaumEtAl2014,ChanfreutEtAl2018}.
Still, since we are interested in resource constraints and the dual decomposition does not enforce local feasibility~\cite{BoydEtAl2015}, the primal decomposition is chosen.

\subsection{Distributed Model Predictive Control}\label{ssec:dMPC}

\newcommand{\masterpb}{\emph{master problem}}
The technique consists of decomposing the \emph{coupling constraints} (or \emph{complicating constraints}~\cite{BoydEtAl2015}) of the original optimization problem into local versions with additional variables
that are shared among them, negotiating the value of these variables until a consensus is reached.

Problem~\ref{Pb:GOP} is decomposed into multiple subproblems~\eqref{eq:DOP_local}, solvable in parallel, and a \masterpb~\eqref{eq:DOP_master}, which is equivalent to the original problem and uses information of the subproblems~\cite{BoydEtAl2015}:

  \begin{subequations}
    \begin{equation}
      \left.
        \small
        \begin{aligned}
          J_{i}^{\star}(\vec{\theta}_{i}(k))&=\underset{\vec{u}_{i}(k:k+N_{p}-1|k)}{\mathrm{minimize}}J_i(k)\\
          \mathrm{s.t.} &\quad\eqref{eq:systems}\\
          &\quad\Gamma_{i}\vec{u}_i(k)=\vec{\theta}_{i}(k):\vec{\lambda}_{i}(k)\\
        \end{aligned}
      \right\}
      \small
        \begin{aligned}
      &\forall i\in\{1,\dots,M\}\\
      &\forall j\in\{1,\dots,N_{p}\}
        \end{aligned}
      \label{eq:DOP_local}
    \end{equation}
    \begin{equation}
      \small
      \begin{aligned}
        J^{\star}&=\underset{\vec{\theta}(k:k+N_{p}-1|k)}{\mathrm{minimize}}\sum^{M}_{i=1} J^{\star}_i(\vec{\theta}_i(k))\\
        \mathrm{s.t.} &\quad \sum_{i=1}^{M}\vec{\theta}_{i}(k)=\vec{u}_{\max}
      \end{aligned}
      \label{eq:DOP_master}
    \end{equation}
  \end{subequations}

The subproblems~\eqref{eq:DOP_local} are formed by the local objectives $J_i(k)$  and a set of local constraints, with a sequence of allocations $\vec{\theta}_{i}(k:k+N_{p}-1|k)$ and associated sequence of dual variables (Lagrange multipliers) $\vec{\lambda}_{i}(k:k+N_{p}-1|k)$.
For brevity's sake, we drop the $(k:k+N_{p}-1|k)$ sequence notation, using only where pertinent.

The variables $\vec{\theta}_{i}$ represent the resource or the ``quantity'' allocated for each subproblem; thus, the names \mbox{``quantity decomposition''} and \mbox{``resource allocation''} are also given for this decomposition~\cite{Cohen1978}.

The \emph{master problem} shown in~\eqref{eq:DOP_master} can be solved using an iterative method that updates the allocation sequence $\vec{\theta}_{i}$.

Due to the form of the constraints, we use the projected sub-gradient method whose recurrence
equation is:
\begin{equation}
  \label{eq:projectedSubgradient}
\vec{\theta}^{(p+1)}=P_{\mathsf{H}}(\vec{\theta}\p-\rho\p\vec{g}\p)
\end{equation}
where ${\mathsf{H} = \enstq{\vec{\theta}}{\sum_{i=1}^{M}\vec{\theta}_{i}=\vec{u}_{\max}}}$, $\vec{g}\p$ is a sub-gradient of $J^{\star}(\vec{\theta}\p)$ at the instant $p$ and $\rho\p$ is an iteration step, well-chosen, so the method converges.

The sum $\sum_{i=1}^{M}\vec{\theta}_{i}$ can also be represented by the matrix multiplication $I_{c}^{M}\vec{\theta}$, where ${I_{c}^{M}=\1_{M,1}\otimes I_{c}}$. Where ${c=\pi_{\vec{u}_{i}(k:k+N_{p}-1|k)}=N_{p}\pi_{\vec{u}_{i}(k)}}$.

Assuming \emph{strong duality} holds, we can use the sensitivity analysis of the problem~\cite[\S~5.6.2]{BoydVandenberghe2004}, and we can conclude that the opposite of the sequences of optimal dual variables, $-\vec{\lambda}^{\star}_{i}$, which are $\vec{\theta}_{i}\p$ dependent, is a sub-gradient of $J_{i}^{\star}(\vec{\theta}_{i}\p)$, which can be used in~\eqref{eq:projectedSubgradient} to solve the problem~\eqref{eq:DOP_master}.

Applying the Euclidean projection onto $\mathsf{H}$~\cite{Ouyang2020} and using $-\vec{\lambda}_{i}^{\star}(\vec{\theta}_{i}\p)$ in~\eqref{eq:projectedSubgradient} results in the complete expression for the allocation's update~\cite[\S VI-C]{Cohen1978}:
\begin{equation}
  \label{eq:thetaNegot}
  \resizebox{0.45\textwidth}{!}{$
  \begin{aligned}
\vec{\theta}_{i}\pplusone=\vec{\theta}_{i}\p+\rho\left(\vec{\lambda}_{i}^{\star}(\vec{\theta}_{i}\p)-I_{c}^{M}{({I_{c}^{M}}\T I_{c}^{M})}^{-1}{I_{c}^{M}}\T \vec{\lambda}^{\star}(\vec{\theta}\p)\right)
  \end{aligned}$}
\end{equation}

In each step $(p)$, the subproblems receive a sequence of  allocation of the total resources.
Then they return their corresponding sequence of dual variables so the \emph{master problem} can be solved by updating the allocations, recommencing the negotiation.
Once a consensus is reached, the negotiation is finished, each subsystem takes the last sequence of inputs $\vec{u}_{i}^{\star}(k:k+N_{p}-1|k)$ calculated and applies the first element $\vec{u}_{i}^{\star}(k|k)$, following a receding horizon strategy.

Delegating the iterative process of allocation update to an agent with the \emph{coordinator}'s role, we have the scheme in Fig.~\ref{fig:schemeQuantity} that illustrates the negotiation.
Observe that each block \emph{negot} solves~\eqref{eq:thetaNegot} for a respective agent $i$.
This way, the only interaction that the \emph{coordinator} has with the subsystems is via the variables $\vec{\lambda}_{i}\p$ and $\vec{\theta}_{i}\pplusone$, increasing the privacy of the subsystems.
\begin{figure}[!t]
  \centering
 \footnotesize \def\svgwidth{0.44\textwidth} \input{./img/diagQuantMod.pdf_tex}
 \caption{Scheme of DMPC using a \emph{coordinator} and $M$ agents.}\label{fig:schemeQuantity}
\end{figure}

Algorithm~\ref{alg:quantityAlg} resumes the distributed control problem solved to calculate the optimal input sequence at each time $k$ using quantity decomposition.
\begin{algorithm}[!t]
  \DontPrintSemicolon
  Coordinator initializes $\vec{\theta}^{(0)}$ \;
  $p:=0$\;
  \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
  Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;
  Coordinator updates allocations~\eqref{eq:thetaNegot}\;
  $p:=p+1$
}
 \caption{Quantity decomposition based DMPC.}\label{alg:quantityAlg}
\end{algorithm}

\section{Attack in DMPC scheme}\label{sec:attack}

As expected~\cite{BoydEtAl2015,Cohen1978}, this decomposition method works well when each agent cooperatively calculates its $\vec{\lambda}_{i}$ correctly.
Here we study the effects when an ill-intentioned agent exploits the scheme for its interest.

\cite{VelardeEtAl2017,VelardeEtAl2017a,ChanfreutEtAl2018,AnandutaEtAl2020} present 4 types of attacks, which can be divided into 2 principal groups: changes in the optimization parameters (\emph{selfish attack} - multiply the objective function by a scalar~$\alpha$, \emph{fake reference}, and \emph{fake constraints}) and nonagreed control (\emph{liar agent}).
In the decomposition scheme used in this work, the coordinator allocates the resources.
So we can discard the last kind of attack.

Although we could make the same analysis from the mentioned works, we are interested in the coordinator's point of view, so any of these attacks will reflect as a change on the $\vec{\lambda}_{i}$ received.
Therefore, we propose that any selfish agent sends a
corrupted
\begin{equation}\label{eq:cheating}
\tilde{\vec{\lambda}}_{i}=\gamma_{i}(\vec{\lambda}_{i})
\end{equation}
to the coordinator instead of sending the agreed $\vec{\lambda}_{i}$.

We give a unidimensional example where ${\gamma_{i}(\lambda_{i})=\tau_{i}\,\lambda_{i}}$ to illustrate such an attack.
Here, 4 agents negotiate with the coordinator, and agent 1 attacks the system ($\tau_{1}\neq1$).

In Fig.~\ref{fig:Jagainsttau}, we see that when ${\tau_{i}>1}$, agents 1's local cost $J_{1}^{\star}$ decreases while all other costs, including the overall $J^{\star}$, increase.
This attack is comparable to the \emph{selfish attack} portrayed in~\cite{VelardeEtAl2017}.
This decrease in the cost justifies the attack since the attacking agent has more comfort than all others.

On the other hand, when $\tau_{1}$ tends to $0$, $J_{1}^{\star}$ increases and all others $J_{i}$ decreases, while still degrading the overall cost $J^{\star}$.
Such an agent could be considered as a benevolent agent or an agent attacked by a malevolent one.

From this variation in the values of $\vec{\lambda}_{1}$ caused by $\tau_{1}$, we can interpret its role in the negotiation: the values of $\vec{\lambda}_{i}$ represent the dissatisfaction with the given allocation $\vec{\theta}_{i}$.

Since the negotiation~\eqref{eq:thetaNegot} finds its stability when ${\vec{\lambda}\p-{I_{c}^M}{({I_{c}^M}\T {I_{c}^M})}^{-1}{I_{c}^M}\T\vec{\lambda} \p=\vec{0}}$, that means when all $\vec{\lambda}_{i}$ are equal to the mean of the $\vec{\lambda}_{i}$.
We can interpret that the coordinator's role is to minimize the overall dissatisfaction.
This way, the selfish agent can lie about its dissatisfaction (increasing $\vec{\lambda}_{i}$ by using an adequate $\gamma_{i}(\cdot)$), driving the negotiation to a value of $\vec{\theta}_{i}$ that ``satisfies'' it more (lower optimal value $J_{i}^{\star}$).

Another effect we can expect from the observation of~\eqref{eq:thetaNegot} is that the negotiation may not converge for some values of $\vec{\lambda}_{i}$. We can find those values by the analysis of the eigenvalues of the iterative process. This effect is illustrated in the hatched area in Fig.~\ref{fig:Jagainsttau}.

\begin{figure}[!t]
  \centering
  \includegraphics[width=\linewidth]{changeOfJ.pdf}
  \caption{Change of $J^{\star}$ with respect to the non-cooperative coefficient $\tau_1$.}\label{fig:Jagainsttau}
\end{figure}

\section{Secure DMPC based on resource allocation}\label{sec:mitigation}

As seen, a malicious agent can deviate the allocations for its benefit, driving the negotiation or even destabilizing it.
Hence, it is needed to find a way to lessen the effects caused by this agent.
To fill this gap, we propose a detection and mitigation mechanism to reduce the effects of any agent malfeasance in the negotiation.
However, before presenting the mechanism, we need to analyze the problem structure to sustain the proposition.
\subsection{Quadratic Case --- Formal Analysis}\label{ssec:FA}
Another known form to represent the problems~\eqref{eq:DOP_local} is using matrix representation~\cite{ChanfreutEtAl2018}:
\begin{equation}
\begin{matrix}
\underset{\vec{U}_i(k)}{\mathrm{minimize}}& \overbrace{\frac{1}{2}{\vec{U}_i(k)}^T H_i\vec{U}_i(k)+{\vec{f}_i(k)}^T\vec{U}_i(k)}^{\textstyle J_{i}(\vec{\theta}_{i})}\\
\mathrm{s.t.}&\Theta_{i}\vec{U}_i(k)=\vec{\theta}_{i}:\vec{\lambda}_{i}\\
\end{matrix}
\label{eq:dmpcModLOP}
\end{equation}
If we take reference tracking, for instance, we have:
\begin{equation}
\small\begin{matrix*}[l]
 H_i&=&\mathcal{D}_i^T\bar{Q}_i\mathcal{D}_i+\bar{R}_i\\
\vec{f}_i(k)&=&\mathcal{D}_i^T\bar{Q}_i(\mathcal{M}_i\vec{x}_i(k)-\vec{W}_i(k))\\

\end{matrix*}
\label{eq:matrices}
\end{equation}
The input and setpoint predictions for times ${k}$ to ${k+N_{p}}$ calculated in time $k$ are adequately stacked in vectors $\vec{U}_{i}(k)$ and $\vec{W}_{i}(k)$.
${\mathcal{M}_{i}}$  and ${\mathcal{D}_{i}}$ are the prediction matrices of the MPC\@.
$\bar{Q}_{i}$, $\bar{R}_{i}$, and $\Theta_{i}$ are block diagonal matrices built repeating $N_{p}$ times $Q_{i}$, $R_{i}$, and $\Gamma_i$ respectively.

Notice that the matrices $H_{i}$ are not only symmetric positive definite, but they are also \mbox{time-invariant}, unlike the $\vec{f}_{i}(k)$, which depend on $x_{i}(k)$ and $\vec{W}_{i}(k)$.

Observe that since $J_{i}(\vec{\theta}_{i})$ is quadratic, we can get an explicit  solution for its dual variables $\vec{\lambda}_{i}$, which are affine with respect to $\vec{\theta}_{i}$:
\begin{equation}
  \begin{aligned}
    \label{eq:lambdafuntheta}
    \vec{\lambda}_{i}=-P_{i}\vec{\theta}_{i}-\vec{s}_{i}(k)
  \end{aligned}
\end{equation}
where ${P_{i}={(\Theta_{i}H_{i}^{-1}\Theta_{i}\T)}^{-1}}$ and ${\vec{s}_{i}(k)=P_{i}\Theta_{i}H_{i}^{-1}\vec{f}_{i}(k)}$.
We can observe that $P_{i}$ are symmetric and depend only on $\Theta_{i}$ and $H_{i}$, which are time-invariant.

\subsection{Detection and mitigation}
In this secure scheme, the exchange between coordinator and agents  is divided into two parts: first, to detect any misbehavior, and second, the negotiation itself, which limits the effects of eventual attacks.

\begin{assumption}
  $\gamma_{i}(\cdot)$ is the same during the negotiation phase for a given time $k$ (it does not depend on $p$).
\end{assumption}

\begin{assumption}
  We suppose the agent chooses a linear function such as
  \begin{equation}
    \label{eq:linear_cheating}
    \tilde{\vec{\lambda}_{i}}=\gamma_{i}(\vec{\lambda}_{i})=T_{i}(k)\vec{\lambda}_{i}
       =-T_{i}(k)P_{i}\vec{\theta}_{i}-T_{i}(k)\vec{s}_{i}(k),
  \end{equation}
and we define $\tilde{P}_{i}(k)=T_{i}(k)P_{i}$ and $\tilde{\vec{s}}_{i}(k)=T_{i}(k)\vec{s}_{i}(k)$.
\end{assumption}

Given that $P_{i}$ does not change from time to time, we can use the relation between $\vec{\theta}_{i}$ and $\vec{\lambda}_{i}$, shown in~\eqref{eq:lambdafuntheta}, to find estimates $\widehat{\tilde{P}}_{i}(k)$ such as:
\begin{equation}
  \label{eq:lambdafuntheta_tilde}
\tilde{\vec{\lambda}_{i}}=\gamma_{i}(\vec{\lambda}_{i}(\vec{\theta}_{i}))=-\widehat{\tilde{P}_{i}}(k)\vec{\theta}_{i}-\widehat{\tilde{\vec{s}}}_{i}(k)
\end{equation}

\begin{remark}
If the estimation does not converge, necessarily there has been a change in $P_{i}$ since the relation between $\vec{\lambda}_{i}$ and $\vec{\theta}_{i}$ has ceased to be affine.

\end{remark}

If we estimate $\widehat{\tilde{P}}_{i}(k)$ for two different times $k$ and they differ, then there has been a change in behavior in agent $i$.

\begin{assumption}\label{ass:Pnominal}
  We have access to the nominal value of $P_{i}$, denoted $\bar{P}_{i}$, from reliable attack-free historical data.
\end{assumption}

Using this strategy, we can detect a deviation from nominal behavior using ${E_{i}(k) =\|\widehat{\tilde{P}}_{i}(k)-\bar{P}_{i}\|_{F}}$, where ${\|\cdot\|_{F}}$ is the Frobenius norm.
Let ${d_{i}\in\{0,1\}}$ be an indicator that detects the attack in agent $i$.
If the disturbance $E_{i}(k)$ respects an arbitrary bound
\begin{equation}
  \label{eq:2}
  E_{i}(k)\leq\epsilon_{P},
\end{equation}
then  ${d_{i}=0}$, and no attack is detected. Otherwise, ${d_{i}=1}$, and a change in behavior of agent $i$ is detected.

If the attack is detected and we want to counteract the change in $\vec{\lambda}_{i}$, one strategy would be to recover $\vec{\lambda}_{i}$ from an inverse of $\gamma_{i}(\cdot)$.

\begin{assumption}
We suppose ${\tilde{\vec{\lambda}}_{i}=\vec{0}}$ only if ${\vec{\lambda}_{i}=\vec{0}}$, which implies $T_{i}(k)$ invertible.
\end{assumption}

Using these assumptions, we can try to estimate the inverse of $T_{i}(k)$ as in  \begin{equation}\label{eq:5}
{\widehat{T_{i}(k)^{-1}}=\bar{P}_{i}\widehat{\tilde{P}_{i}}(k)^{-1}},
\end{equation}
and from~\eqref{eq:lambdafuntheta}, we can derive a method to reconstruct $\vec{\lambda}_{i}$:
\begin{equation}
  \label{eq:lambdareconstruction}
  {\vec{\lambda}_{i}}_{\mathrm{rec}}=\widehat{T_{i}(k)^{-1}} \tilde{\vec{\lambda}_{i}} =-\bar{P}_{i}\vec{\theta}_{i}-\widehat{{T_{i}(k)^{-1}}}\widehat{\tilde{\vec{s}}}_{i}(k).
\end{equation}
Notice that we also need $\widehat{\tilde{\vec{s}}}_{i}(k)$ to use this reconstruction.

This reconstructed ${\vec{\lambda}_{i}}_{\mathrm{rec}}$ can be used in~\eqref{eq:thetaNegot}. Observe that, as~\eqref{eq:lambdareconstruction} does not depend on $\tilde{\vec{\lambda}}_{i}$, the rest of the negotiation process takes place without taking the attacking agent's responses into account.

In case no attack is detected, the coordinator can use the $\tilde{\vec{\lambda}_{i}}$ during the negotiation phase.

This mechanic of detecting and choosing which version of $\vec{\lambda}$ to use during the negotiation, corresponds to the inclusion of a supervisor for each agent (Fig.~\ref{fig:schemeSafeQuantity}),

Observe in Fig.~\ref{fig:schemeSafeQuantity} that the coordinator sends $\mathring{\vec{\theta}}_{i}$ to the agents. These values may be the ones from the negotiation or other. The reason to send different values is discussed in the following subsection.
\begin{figure}[b]
  \centering
  \scriptsize \def\svgwidth{0.49\textwidth}
\input{img/diagQuantSafe2.pdf_tex}
  \caption{Scheme for Secure DMPC}\label{fig:schemeSafeQuantity}
\end{figure}

\subsection{Considerations about parameter estimation}

As seen, we need to estimate $\tilde{P}_{i}(k)$ and $\tilde{\vec{s}}_{i}(k)$.
This estimation is achieved by the relation between $\vec{\theta}_{i}$ and $\vec{\lambda}_{i}$ shown in~\eqref{eq:lambdafuntheta}.
As we suppose there is no noise in the communication, we propose to use Recursive Least Squares (RLS) with a forgetting coefficient $\phi$ to find simultaneously unbiased estimates of $\tilde{P}_{i}(k)$ and $\tilde{\vec{s}}_{i}(k)$.

If we try to estimate during the negotiation, the estimation will fail since consecutive values of $\vec{\lambda}_{i}^{p}$ and $\vec{\theta}_{i}^{p}$ are necessarily linearly dependent~\eqref{eq:thetaNegot}, and estimators become badly scaled. This fact is known and is described as low input excitation~\cite[\S 5]{AastroemWittenmark1989}.
As a counter-measure, to enrich the input excitation, the coordinator sends a sequence of random values of $\vec{\theta}_{i}$ until the estimation converges. It then resumes the typical negotiation, eventually using the mitigation mechanism if an attack is detected.

\begin{assumption}\label{ass:tildePinvertible}
Since $P_{i}$ is expected to be symmetric~\eqref{eq:lambdafuntheta}, we suppose that the attacker chooses a $T_{i}(k)$ that does not change the structure of the resulting matrix, so it can not be discovered.
In this case, we assume $\tilde{P}_{i}(k)$ symmetric and invertible.
\end{assumption}
As $\tilde{P}_{i}(k)$ is symmetric, we estimate only the upper triangle, reducing the number of estimated parameters from $\pi_{\tilde{P}_{i}(k)}$ to $\frac{\pi_{\tilde{P}_{i}(k)}+\sqrt{\pi_{\tilde{P}_{i}(k)}}}{2}$, and consequently the length of the estimation sequence~\cite{AastroemWittenmark1989}.

We stack the elements of $\widehat{\tilde{P}}_{i}(k)$ and $\widehat{\tilde{\vec{s}}}_{i}(k)$ estimated in a step $h$ in vectors $\eta_{i}^{h}$. The estimation converges when
${\|\eta_{i}^{h}-\eta_{i}^{h-1}\|\leq\epsilon}$,
with $\epsilon$ arbitrarily small.

\subsection{Secure DMPC}
\label{sec:secure-dmpc}
After all the reflections about parameter estimation and the detection and mitigation mechanism, we can finally propose a secure DMPC based on the reconstruction of $\vec{\lambda}_{i}$.

Algorithm~\ref{alg:safeDMPC} summarizes the process used to find the optimal inputs $\vec{u}_{i}^{\star}(k|k)$ to be applied at each time $k$.
We can see the two phases: the detection phase, where the coordinator detects if the system is attacked and by which agent. And the second phase, where the usual negotiation in algorithm~\ref{alg:quantityAlg} takes place, using different values of $\vec{\lambda}_{i}$ depending on if the respective agent is an attacker.

In the next section, we present an example to illustrate the performance of the mechanism.
\SetKwBlock{negotPhase}{ Negotiation Phase:}{}
\SetKwBlock{detectPhase}{ Detection Phase:}{}
\begin{algorithm}[h]
  \DontPrintSemicolon
  \detectPhase{
  $h:=0$\;
    \Repeat{
$\|\eta_{i}^{h}-\eta^{h-1}\|\leq\epsilon$
}{
    Coordinator sets random $\vec{\theta}_{i}^{(h+1)}$ \;
    Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}^{(h)})$\;
    Coordinator estimates $\widehat{\tilde{P}}_{i}(k)^{(h)}$ and $\widehat{\tilde{\vec{s}}}_{i}(k)^{(h)}$ \;
    $h:=h+1$\;
    }
    Coordinator computes $d_{i}$ using~\eqref{eq:2}\;
  }
  \negotPhase{
  Coordinator initializes $\vec{\theta}^{(0)}$ \;
  $p:=0$\;

  \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
  Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;

  Coordinator updates allocation~\eqref{eq:thetaNegot} using adequate versions of $\vec{\lambda}_{i}$ for each agent: $\vec{\lambda}_{i}^{\star}(\vec{\theta}\p)$, if $d_{i}=0$ and ${\vec{\lambda}_{i}}_{\mathrm{rec}}$, if ${d_{i}=1}$\;
  $p:=p+1$
 }}
 \caption{Secure DMPC.}\label{alg:safeDMPC}
\end{algorithm}

\section{Example: Temperature Control}\label{sec:App_dMPC}
In this example, we want to control the temperature of 4~distinct~rooms (called I, II, III, and IV) under power scarcity using quantity decomposition.
The systems are modeled as continuous-time linear \mbox{time-invariant} systems using the \mbox{3R-2C} model~\cite{GoudaEtAl2002}.

The state-space model of each subsystem is given by:
\begin{equation}
\begin{matrix}
  \dot{\left[\begin{matrix} {\vec{x}_{A}}_{i}\\ {\vec{x}_{W}}_{i} \end{matrix} \right]}
  =\dot{\vec{x}}_{i}=A_{\mathrm{c}_{i}}\vec{x}_{i}+B_{\mathrm{c}_{i}}\vec{u}_{i}\\
\vec{y}_{i}=C_{\mathrm{c}_{i}}\vec{x}_{i}
\end{matrix}
\end{equation}
where
\begin{equation}
  \label{eq:4}
  \begin{matrix}
  A_{\mathrm{c}_{i}}=\left[
    \begin{matrix}
      -\frac{1}{C_{\mathrm{res}_{i}}Rf_{i}}-\frac{1}{C_{\mathrm{res}_{i}}Ri_{i}}& \frac{1}{C_{\mathrm{res}_{i}}Ri_{i}}\\
      \frac{1}{Cs_{i}Ri_{i}} &-\frac{1}{Cs_{i}Ro_{i}}-\frac{1}{Cs_{i}Ri_{i}}
    \end{matrix}\right]\\
  \begin{matrix}
    B_{\mathrm{c}_{i}}=\left[
      \begin{matrix}  \frac{10}{C_{\mathrm{res}_{i}}}& 0\end{matrix}
    \right]\T&C_{\mathrm{c}_{i}}=\left[\begin{matrix}1 & 0\end{matrix}\right]
  \end{matrix}
  \end{matrix}
\end{equation}

We can see the meaning and the values of its parameters in tables~\ref{tab:modelParamMeaning} and~\ref{tab:modelParam}.

\begin{table}[b]
  \centering
  \caption{Model Parameters Meanings}\label{tab:modelParamMeaning}
  \begin{tabular}[b]{cl}
    \toprule
    Symbol&Meaning\\
    \midrule
    $C_{\mathrm{res}_{i}}$&Heat Capacity of Inside Air\\
    $Cs_{i}$&Heat Capacity of External Walls\\
    $Rf_{i}$&Resistance Between Inside and Outside Air (from windows)\\
    $Ri_{i}$&Resistance Between Inside Air and Inside Walls\\
    $Ro_{i}$&Resistance Between Outside Air and Outside Walls\\
    \bottomrule
  \end{tabular}
\end{table}
\begin{table}[b]
  \centering
  \caption{Model Parameters Values}\label{tab:modelParam}
  \begin{tabular}[t]{cccccc} \toprule
    Symbol& I & II & III & IV &Unit\\
    \midrule
    $C_{\mathrm{res}}$    &$5$   & $4$ & $4.5$ &$4.7$ &$10^{4}\mathrm{J/K}$ \\
    $Cs$               &$8$   & $7$ &$9$&$6$  &$10^{4}\mathrm{J/K}$  \\
    $Rf$               &$5$   & $6$& $4$& $5$  &$10^{-3}\mathrm{K/W}$ \\
    $Ri$               &$2.5$ & $2.3$&$2$&$2.2$ &$10^{-4}\mathrm{K/W}$\\
    $Ro$               &$0.5$ & $1$ &$0.8$&$0.9$  & $10^{-4}\mathrm{K/W}$ \\
    \bottomrule
  \end{tabular}
\end{table}
The states ${\vec{x}_{A}}_{i}$ and ${\vec{x}_{W}}_{i}$ represent the mean temperatures of the air and walls inside room $i$. The input $\vec{u}_{i}$ is the heating power
for the corresponding room.
The global coupling constraint is ${\sum_{i=1}^{4}\vec{u}_{i}(k)=4\mathrm{kW}}$.

The subsystems are discretized using the zero-order hold discretization method with sampling time
${T_{s}=0.25\mathrm{h}}$
and the quantity decomposition-based DMPC is implemented using prediction horizon ${N_{p}=4}$.

Three scenarios are simulated for a period of 5 hours:

  \begin{enumerate}
    \item Nominal behavior.
    \item \mbox{Agent I presents constant non-cooperative behavior} ${T_{I}(k)=4\,I_{\sqrt{\pi_{P_{I}}}}}$ for ${k\geq6}$, without correction.
    \item \mbox{Agent I presents constant non-cooperative behavior} ${T_{I}(k)=4\,I_{\sqrt{\pi_{P_{I}}}}}$ for ${k\geq6}$, with correction, ${\epsilon_{P}=10^{-4}}$.
  \end{enumerate}

In Fig.~\ref{fig:response3Scenarios}, first, we compare the output of the agent I
(air temperature in the room) with its reference ($20^{\circ}$C), and then the
decision variable ${E_{I}(k)}$ with the threshold $\epsilon_{P}$.
All the 3 scenarios above are represented with indices N (for nominal), S (for selfish), and C (for corrected).

\begin{figure}[t]
  \centering
  \includegraphics[width=7cm]{AirTempAndDecisionVariable.pdf}
\caption{Air temperature in room I and the decision variable $E_{I}(k)$ for
different scenarios: nominal (N), with selflish behavior without correction (S)
and with selfish behavior with correction (C)}\label{fig:response3Scenarios}
\end{figure}
Observe that in the nominal behavior, the reference $w_{I}$ is not reached
due to power scarcity since we deliberately set a total power not sufficient to
satisfy the needs of each agent.
As expected, the decision variable lies under the threshold $\epsilon_{P}=10^{-4}$ with values of order ${E_{I}^{N}(k)\approx10^{-10}}$.

When the agent presents a selfish behavior, the tracking error
${w_{I}-y_{I}}$ is reduced but insufficient to attain the reference.
In this case, the detection variable surpasses $\epsilon_{P}$,
${E_{I}^{S}=9.762}$, indicating the change of behavior of agent I.

When the correction is activated in the system, we see that the corrected
$y_{I}^{C}$ approaches the nominal value $y_{I}^{N}$, illustrating the good
performances of our proposition.

We can also evaluate the performance of the proposed mechanism by comparing the
local and global costs calculated using the initial cost function presented
in~\eqref{eq:dmpcModLOP} using N as the total period of simulation, ${N=20}$.
The same 3 scenarios are compared in table~\ref{tab:costsGlobalLocal}.

As in Section~\ref{sec:attack}, when agent I is selfish, we see the decline of its cost at the expense of increasing all other costs. This increase in cost degrades the global objective.
When the correction mechanism is activated, the differences between costs are minimal, and the global cost stays close to the nominal value, highlighting the mechanism's performance.
%%%%%
\begin{table}[t]
  \centering
  \caption{Comparison of costs $J_{i}^{N}$ and $J_{G}^{N}$}\label{tab:costsGlobalLocal}
  \begin{tabular}[t]{cccc} \toprule
    Agent  & Nominal & Selfish & Selfish + correction\\
    \midrule
    I      & 103  &  64  & 104  \\
    II     &  73  &  91  &  73  \\
    III    & 100  & 123  & 101  \\
    IV     & 132  & 154  & 131  \\
    Global & 408  & 442  & 409  \\
    \bottomrule
  \end{tabular}
\end{table}
\enlargethispage{-.8cm}

\section{CONCLUSION AND FUTURE WORKS}\label{sec:CC}

In this paper, an algorithm for monitoring and correcting exchanges between agents in a resource-sharing system has been proposed.
The algorithm exploits the particular structure of exchanges, part of which must be constant over time.
The first phase consists of identifying this constant part and checking if an attacker has modified it.
From this identification, it is possible to reconstruct the original mechanism and find the centralized optimality.
This principle should be generalized to other types of decomposition structures, and this is what we plan to do in the near future.

\section{ACKNOWLEDGMENTS}\label{sec:ACK}

The authors would like to acknowledge C. R. Sorgho for her preliminary results.
% Balance https://blog.narf.ssji.net/2014/05/twocolumn-balancing-latex/
% \IEEEtraggeratref{PaulenEtAl2016}

\bibliographystyle{IEEEtran}
\bibliography{bibliography}

%%%%%
\end{document}

### 2021-08-26 article/article.tex
add IEEE copyright

@@
 \geometry{
-  textwidth=\columnwidth,
   top=19.1mm,
@@
 
-\draft%
-% \final%
-
-\makeglossaries
+% \draft%
+\final%
+\newcommand{\id}{}
+\newcommand{\price}{31.00}
+\pubid{\begin{minipage}{\textwidth}\ \\[50pt]\centering
+  \copyright 2021 IEEE. Personal use is permitted, but republication/redistribution requires IEEE permission.\\
+See https://www.ieee.org/publications/rights/index.html for more information.
+\end{minipage}}
+% \makeglossaries
+\markboth{Oi}{test}
 \begin{document}
@@
 % \IEEEpeerreviewmaketitle% This command is only
-\thispagestyle{empty}
-\pagestyle{empty}
+% \thispagestyle{empty}
+% \pagestyle{empty}
 
@@
 \section{PRELIMINARIES AND PROBLEM STATEMENT}\label{sec:PS}
-\emph{Notation:} In this paper, $\|\cdot\|$ and $\|\cdot\|_{F}$ represent the $\ell_{2}$ and Frobenius norms. $\|\vec{v}\|_{Y}$ is the weighted norm, $\|Y^{1\over 2}\vec{v}\|$.
+\emph{Notation:} In this paper, $\|\cdot\|$ and $\|\cdot\|_{F}$ represent the $\ell_{2}$ and Frobenius norms. $\|\vec{v}\|_{Y}$ is the weighted norm, $\|Y^{\frac{1}{2}}\vec{v}\|$.
 $P_{\mathsf{T}}(\cdot)$ is the Euclidean projection onto set $\mathsf{T}$.
@@
 \end{matrix}
-\label{eq:dmpcModLOP}
+% \label{eq:dmpcModLOP}
 \end{equation*}

### 2021-08-30 presentation/presentation.tex
add presentation

% $Header$

\documentclass[aspectratio=169]{beamer}

% This file is a solution template for:

% - Talk at a conference/colloquium.
% - Talk length is about 20min.
% - Style is ornate.

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

\mode<presentation>
{
  \usetheme{Warsaw}
  % or ...

  \setbeamercovered{transparent}
  % or whatever (possibly just delete it)
}

\usepackage[english]{babel}
% or whatever

\usepackage[utf8]{inputenc}
% or whatever

\usepackage{times}
\usepackage[T1]{fontenc}
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.

\title[Detect. and Mitigation of Corrupted Info. in DMPC Based on Resource Allocation] % (optional, use only with long paper titles)
{Detection and Mitigation of Corrupted Information in Distributed Model Predictive Control Based on Resource Allocation}

% \subtitle
% {Include Only If Paper Has a Subtitle}

\author[Nogueira, Bourdais, Guéguen] % (optional, use only with lots of authors)
{R. A. Nogueira \and R. Bourdais \and H. Guéguen}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[IETR --- CentraleSupélec] % (optional, but mostly needed)
{
  % \inst{1}%
  AUT Department\\
  IETR --- CentraleSupélec
}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date[SysTol'21] % (optional, should be abbreviation of conference name)
{5th International Conference on Control and Fault-Tolerant Systems, 2021
                      \includegraphics[width=2cm]{../img/qrPresentation.png}
}
% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

\subject{}
% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

\pgfdeclareimage[height=0.5cm]{university-logo}{../img/logos/supelec.jpeg}
\logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSubsection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

% If you wish to uncover everything in a step-wise fashion, uncomment
% the following command:

%\beamerdefaultoverlayspecification{<+->}

\begin{document}

\begin{frame}[plain]
  \titlepage
\end{frame}

\begin{frame}{Outline}
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

% Structuring a talk is a difficult task and the following structure
% may not be suitable. Here are some rules that apply for this
% solution:

% - Exactly two or three sections (other than the summary).
% - At *most* three subsections per section.
% - Talk about 30s to 2min per frame. So there should be between about
%   15 and 30 frames, all told.

% - A conference audience is likely to know very little of what you
%   are going to talk about. So *simplify*!
% - In a 20min talk, getting the main ideas across is hard
%   enough. Leave out details, even if it means being less precise than
%   you think necessary.
% - If you omit details that are vital to the proof/implementation,
%   just say so once. Everybody will be happy with that.

\section{Motivation}

\subsection{The Basic Problem That We Studied}

\begin{frame}{Make Titles Informative. Use Uppercase Letters.}{Subtitles are optional.}
  % - A title should summarize the slide in an understandable fashion
  %   for anyone how does not follow everything on the slide itself.

  \begin{itemize}
  \item
    Use \texttt{itemize} a lot.
  \item
    Use very short sentences or short phrases.
  \end{itemize}
\end{frame}

\begin{frame}{Make Titles Informative.}

  You can create overlays\dots
  \begin{itemize}
  \item using the \texttt{pause} command:
    \begin{itemize}
    \item
      First item.
      \pause
    \item
      Second item.
    \end{itemize}
  \item
    using overlay specifications:
    \begin{itemize}
    \item<3->
      First item.
    \item<4->
      Second item.
    \end{itemize}
  \item
    using the general \texttt{uncover} command:
    \begin{itemize}
      \uncover<5->{\item
        First item.}
      \uncover<6->{\item
        Second item.}
    \end{itemize}
  \end{itemize}
\end{frame}

\subsection{Previous Work}

\begin{frame}{Make Titles Informative.}
\end{frame}

\begin{frame}{Make Titles Informative.}
\end{frame}

\section{Our Results/Contribution}

\subsection{Main Results}

\begin{frame}{Make Titles Informative.}
\end{frame}

\begin{frame}{Make Titles Informative.}
\end{frame}

\begin{frame}{Make Titles Informative.}
\end{frame}

\subsection{Basic Ideas for Proofs/Implementation}

\begin{frame}{Make Titles Informative.}
\end{frame}

\begin{frame}{Make Titles Informative.}
\end{frame}

\begin{frame}{Make Titles Informative.}
\end{frame}

\section*{Summary}

\begin{frame}{Summary}
  \begin{minipage}{.6\textwidth}
    % Keep the summary *very short*.
    \begin{enumerate}
      \item
            Resource allocation based DMPC is vulnerable to attacks.
      \item
            Sub-problems structure has time invariant parameters.
      \item
            Attack can be estimated using these parameters.
    \end{enumerate}

    % The following outlook is optional.
    \vskip0pt plus.5fill
    \begin{itemize}
      \item
            Outlook
            \begin{itemize}
              \item
                    Inequality Constraints yield Hybrid behavior
              \item
                    Non-linear attack model
            \end{itemize}
      \item Repository

                    \begin{minipage}{.6\textwidth}
                      \url{https://github.com/Accacio/SysTol-21}
                    \end{minipage}
                    \begin{minipage}{.2\textwidth}
                      \includegraphics[width=2cm]{../article/img/qrRepo.png}
                    \end{minipage}
    \end{itemize}
  \end{minipage}
\end{frame}

\nocite{VelardeEtAl2017a}
% All of the following is optional and typically not needed.
\appendix
\section<presentation>*{\appendixname}
\subsection<presentation>*{For Further Reading}

\begin{frame}[allowframebreaks]
\bibliographystyle{IEEEtran}
\bibliography{../article/bibliography}
  \frametitle<presentation>{For Further Reading}

  \begin{thebibliography}{10}

  \beamertemplatebookbibitems
  % Start with overview books.
\bibitem{MaestreEtAl2014}
J.~M. Maestre, R.~R. Negenborn \emph{et~al.}, \emph{{D}istributed {M}odel
  {P}redictive {C}ontrol made easy}.\hskip 1em plus 0.5em minus 0.4em\relax
  Springer, 2014, vol.~69.

  \bibitem{Author1990}
    A.~Author.
    \newblock {\em Handbook of Everything}.
    \newblock Some Press, 1990.

  \beamertemplatearticlebibitems
  % Followed by interesting articles. Keep the list short.

  \bibitem{Someone2000}
    S.~Someone.
    \newblock On this and that.
    \newblock {\em Journal of This and That}, 2(1):50--100,
    2000.
  \end{thebibliography}
\end{frame}

\end{document}

### 2021-08-31 presentation/presentation.tex
update qr code
change color theme

@@
 {
-  \usetheme{Warsaw}
+  \usetheme{Luebeck}
+  % \usetheme{Madrid}
+  % \usetheme{Warsaw}
+  % \usetheme{Copenhagen}
+  % \usecolortheme{beaver}
+  % \usecolortheme{rose}
   % or ...
+  % \usecolortheme{beaver}
+  \useoutertheme{split}
+  \useinnertheme{circles}
 
+  \setbeamercolor{palette primary}{bg=red!50!black!80}
+  \setbeamercolor{palette secondary}{bg=red!50!black!70}
+  \setbeamercolor{palette tertiary}{bg=gray!90!black!50}
+  \setbeamercolor{palette quaternary}{bg=gray!90!black!100}
+
+  \setbeamercolor{item}{fg=red!50!black!80}
+  \setbeamercolor{section in toc}{fg=red!50!black!80}
+
+  % \setbeamercolor{author in head/foot}{bg=grey!60}
   \setbeamercovered{transparent}
+\setbeamertemplate{navigation symbols}{}
+\makeatletter
+\setbeamertemplate{page number in head/foot}[appendixframenumber]
+\setbeamertemplate{headline}
+{%
+  \leavevmode%
+  \hbox{%
+  \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
+    \centering
+    \usebeamerfont{author in head/foot}\insertsection{}
+  \end{beamercolorbox}%
+  \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,right]{title in head/foot}%
+    \centering
+    \insertsubsection{}
+  \end{beamercolorbox}%
+  }%
+  \vskip0pt%
+}
+\setbeamertemplate{footline}
+{%
+  \leavevmode%
+  \hbox{%
+  \begin{beamercolorbox}[wd=.1\paperwidth,ht=2.25ex,dp=1ex,center]{date in head/foot}%
+    \centering
+    \usebeamerfont{date in head/foot}\usebeamercolor[fg]{page number in head/foot}\usebeamerfont{page number in head/foot}\usebeamertemplate{page number in head/foot}
+    % \hspace*{2ex}
+  \end{beamercolorbox}%
+  \begin{beamercolorbox}[wd=.25\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
+    \centering
+    \usebeamerfont{author in head/foot}\insertshortauthor{}
+  \end{beamercolorbox}%
+  \begin{beamercolorbox}[wd=.65\paperwidth,ht=2.25ex,dp=1ex,right]{title in head/foot}%
+    \centering
+    \insertshorttitle{}
+  \end{beamercolorbox}%
+  }%
+  \vskip0pt%
+}
+\makeatother
+
   % or whatever (possibly just delete it)
@@
 
-\usepackage{times}
+% \usepackage{times}
 \usepackage[T1]{fontenc}
@@
 
-\title[Detect. and Mitigation of Corrupted Info. in DMPC Based on Resource Allocation] % (optional, use only with long paper titles)
+\title[Detection and Mitigation of Corrupted Information in DMPC Based on Resource Allocation] % (optional, use only with long paper titles)
 {Detection and Mitigation of Corrupted Information in Distributed Model Predictive Control Based on Resource Allocation}
@@
 \author[Nogueira, Bourdais, Guéguen] % (optional, use only with lots of authors)
-{R. A. Nogueira \and R. Bourdais \and H. Guéguen}
+{R. A. Nogueira \and R. Bourdais \and H. Guéguen\\
+\texttt{\{rafael-accacio.nogueira,romain.bourdais,herve.gueguen\}\ at \ centralesupelec.fr}}
 % - Give the names in the same order as the appear in the paper.
@@
   % \inst{1}%
-  AUT Department\\
-  IETR --- CentraleSupélec
+  AUT Department
+  \\IETR --- CentraleSupélec
+  % \\[10pt]\\\includegraphics[width=1.5cm]{../img/logos/supelec.jpeg}
 }
@@
 
-\pgfdeclareimage[height=0.5cm]{university-logo}{../img/logos/supelec.jpeg}
+\pgfdeclareimage[height=.8cm]{university-logo}{../img/logos/supelec.jpeg}
 \logo{\pgfuseimage{university-logo}}
@@
       \item Repository
+\vspace{-.4cm}
 
@@
                     \begin{minipage}{.2\textwidth}
-                      \includegraphics[width=2cm]{../article/img/qrRepo.png}
+                      \includegraphics[width=2cm]{../img/qrRepo.png}
                     \end{minipage}

### 2021-09-01 presentation/presentation.tex
change color
use includegraphics
add short url
update presentation

@@
 \documentclass[aspectratio=169]{beamer}
-
-% This file is a solution template for:
-
-% - Talk at a conference/colloquium.
-% - Talk length is about 20min.
-% - Style is ornate.
-
-% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
-%
-% In principle, this file can be redistributed and/or modified under
-% the terms of the GNU Public License, version 2.
-%
-% However, this file is supposed to be a template to be modified
-% for your own needs. For this reason, if you use this file as a
-% template and not specifically distribute it as part of a another
-% package/program, I grant the extra permission to freely copy and
-% modify this file as you see fit and even to delete this copyright
-% notice.
 
@@
   \setbeamercolor{palette tertiary}{bg=gray!90!black!50}
-  \setbeamercolor{palette quaternary}{bg=gray!90!black!100}
+  \setbeamercolor{palette quaternary}{bg=gray!90!black!70}
+  \setbeamercolor{block title}{bg=red!50!black!70}
 
@@
   \setbeamercolor{section in toc}{fg=red!50!black!80}
+
+  \setbeamercolor{bibliography entry author}{fg=red!50!black!80}
+  \setbeamercolor{bibliography entry location}{fg=red!50!black!40}
 
@@
 \makeatletter
+\protected\def\protectedempty{}
 \setbeamertemplate{page number in head/foot}[appendixframenumber]
-\setbeamertemplate{headline}
-{%
-  \leavevmode%
-  \hbox{%
-  \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
-    \centering
-    \usebeamerfont{author in head/foot}\insertsection{}
-  \end{beamercolorbox}%
-  \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,right]{title in head/foot}%
-    \centering
-    \insertsubsection{}
-  \end{beamercolorbox}%
-  }%
-  \vskip0pt%
-}
 \setbeamertemplate{footline}
@@
 
+\setbeamertemplate{sidebar right}{
+  \vfill%
+  \llap{\insertlogo\hskip0.2cm}%
+  \vskip3pt%
+  \llap{\usebeamertemplate***{navigation symbols}\hskip0.1cm}%
+  \vskip2pt%
+}
+\setbeamertemplate{headline}
+{%
+  \leavevmode%
+  \hbox{%
+      \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,center]{section in head/foot}%
+      \centering
+      \usebeamerfont{author in head/foot}\insertsection{}
+    \end{beamercolorbox}%
+  % }
+    \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,right]{subsection in head/foot}%
+      \centering
+      \insertsubsection{}
+    \end{beamercolorbox}%
+    }
+  \vskip0pt%
+}
+
   % or whatever (possibly just delete it)
@@
 % does not look nice, try deleting the line with the fontenc.
+
+\usepackage{bm}
+\usepackage[ruled,noend]{algorithm2e}
+\SetKwRepeat{Do}{do}{while}
+
+\newcommand{\eq}[2]{\mbox{$#1=#2$}}
+\newcommand{\N}{\mathbb{N}}
+\newcommand{\Z}{\mathbb{Z}}
+\newcommand{\Q}{\mathbb{Q}}
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\C}{\mathbb{C}}
+\newcommand{\Np}{N_{\text{p}}}
+\newcommand{\T}{^{\mathrm{T}}}
+\newcommand{\1}{\mathbf{1}}
+\newcommand{\0}{\mathbf{0}}
+\newcommand{\abs}[1]{\left\lvert#1\right\rvert}
+\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
+\newcommand{\Varepsilon}{\mathcal{E}}
+\newcommand{\diff}{\mathop{}\mathopen{}\mathrm{d}}
+\newcommand{\set}[1]{\mathcal{#1}}
+\newcommand{\p}{^{(p)}}
+\newcommand{\pplusone}{^{(p+1)}}
+\renewcommand{\vec}[1]{\bm{#1}}
+\newcommand{\enstq}[2]{\{#1\mathrel{}\mid\mathrel{}#2\}}
 
@@
 {5th International Conference on Control and Fault-Tolerant Systems, 2021
-                      \includegraphics[width=2cm]{../img/qrPresentation.png}
+  \begin{minipage}{.3\textwidth}
+    \centering
+    \includegraphics[width=2cm]{../img/logos/logo_IETR.png}
+  \end{minipage}
+  \begin{minipage}{.3\textwidth}
+    \centering
+    \vspace{10pt}
+    \includegraphics[width=1.5cm]{../img/qrPresentation.png}
+    \href{https://git.io/JEFGW}{https://git.io/JEFGW}
+  \end{minipage}
+  \begin{minipage}{.3\textwidth}
+    \centering
+    \vspace{10pt}
+    \includegraphics[width=2cm]{../img/logos/supelec.jpeg}
+  \end{minipage}
 }
@@
 \subject{}
-% This is only inserted into the PDF information catalog. Can be left
-% out.
 
-% If you have a file called "university-logo-filename.xxx", where xxx
-% is a graphic format that can be processed by latex or pdflatex,
-% resp., then you can add a logo as follows:
-
-\pgfdeclareimage[height=.8cm]{university-logo}{../img/logos/supelec.jpeg}
-\logo{\pgfuseimage{university-logo}}
+\logo{\includegraphics[height=.8cm]{../img/logos/supelec.jpeg}}
 
@@
 
-% If you wish to uncover everything in a step-wise fashion, uncomment
-% the following command:
-
-%\beamerdefaultoverlayspecification{<+->}
-
 \begin{document}
@@
 \begin{frame}[plain]
-  \titlepage
+  \titlepage%
+\end{frame}
+
+% \begin{frame}[fragile]
+% \frametitle{An Algorithm For Finding Primes Numbers.}
+% \begin{semiverbatim}
+% \uncover<1->{\alert<0>{int main (void)}}
+% \uncover<1->{\alert<0>{\{}}
+% \uncover<1->{\alert<1>{ \alert<4>{std::}vector<bool> is_prime (100, true);}}
+% \uncover<1->{\alert<1>{ for (int i = 2; i < 100; i++)}}
+% \uncover<2->{\alert<2>{
+% if (is_prime[i])}}
+% \uncover<2->{\alert<0>{
+% \{}}
+% \uncover<3->{\alert<3>{
+% \alert<4>{std::}cout << i << " ";}}
+% \uncover<3->{\alert<3>{
+% for (int j = i; j < 100;}}
+% \uncover<3->{\alert<3>{
+% is_prime [j] = false, j+=i);}}
+% \uncover<2->{\alert<0>{
+% \}}}
+% \uncover<1->{\alert<0>{ return 0;}}
+% \uncover<1->{\alert<0>{\}}}
+% \end{semiverbatim}
+% \visible<4->{Note the use of \alert{\texttt{std::}}.}
+% \end{frame}
+
+\begin{frame}
+\SetKwBlock{negotPhase}{ Negotiation Phase:}{}
+\SetKwBlock{detectPhase}{ Detection Phase:}{}
+\scalebox{.8}{  \begin{algorithm}[H]
+    \DontPrintSemicolon
+    \detectPhase{
+    $h:=0$\;
+    \Repeat{
+    $\|\eta_{i}^{h}-\eta^{h-1}\|\leq\epsilon$
+  }{
+    Coordinator sets random $\vec{\theta}_{i}^{(h+1)}$ \;
+    Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}^{(h)})$\;
+    Coordinator estimates $\widehat{\tilde{P}}_{i}(k)^{(h)}$ and $\widehat{\tilde{\vec{s}}}_{i}(k)^{(h)}$ \;
+    $h:=h+1$\;
+  }
+    Coordinator computes $d_{i}$ using~\eqref{eq:2}\;
+  }
+    \negotPhase{
+    Coordinator initializes $\vec{\theta}^{(0)}$ \;
+    $p:=0$\;
+
+    \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
+    Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;
+
+    Coordinator updates allocation~\eqref{eq:thetaNegot} using adequate versions of $\vec{\lambda}_{i}$ for each agent: $\vec{\lambda}_{i}^{\star}(\vec{\theta}\p)$, if $d_{i}=0$ and ${\vec{\lambda}_{i}}_{\mathrm{rec}}$, if ${d_{i}=1}$\;
+    $p:=p+1$
+  }}
+    \caption{Secure DMPC.}\label{alg:safeDMPC}
+  \end{algorithm}
+  }
+\end{frame}
+
+\begin{frame}
+  \centering
+  \begin{minipage}{.65\linewidth}
+    \begin{algorithm}[H]
+      \DontPrintSemicolon
+      Coordinator initializes $\vec{\theta}^{(0)}$ \;
+      $p:=0$\;
+      \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
+        Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;
+        Coordinator updates allocations~\eqref{eq:thetaNegot}\;
+        $p:=p+1$
+      }
+      \caption{Quantity decomposition based DMPC.}\label{alg:quantityAlg}
+    \end{algorithm}
+  \end{minipage}
 \end{frame}
@@
             \end{itemize}
-      \item Repository
-\vspace{-.4cm}
-
-                    \begin{minipage}{.6\textwidth}
-                      \url{https://github.com/Accacio/SysTol-21}
-                    \end{minipage}
-                    \begin{minipage}{.2\textwidth}
-                      \includegraphics[width=2cm]{../img/qrRepo.png}
-                    \end{minipage}
     \end{itemize}
@@
 % All of the following is optional and typically not needed.
-\appendix
-\section<presentation>*{\appendixname}
-\subsection<presentation>*{For Further Reading}
+% \appendix
+% \section<presentation>*{\appendixname}
+% \subsection<presentation>*{For Further Reading}
 
 \begin{frame}[allowframebreaks]
-\bibliographystyle{IEEEtran}
-\bibliography{../article/bibliography}
+% \bibliographystyle{IEEEtran}
+% \bibliography{../article/bibliography}
   \frametitle<presentation>{For Further Reading}
@@
   \bibitem{MaestreEtAl2014}
-J.~M. Maestre, R.~R. Negenborn \emph{et~al.}, \emph{{D}istributed {M}odel
-  {P}redictive {C}ontrol made easy}.\hskip 1em plus 0.5em minus 0.4em\relax
-  Springer, 2014, vol.~69.
-
-  \bibitem{Author1990}
-    A.~Author.
-    \newblock {\em Handbook of Everything}.
-    \newblock Some Press, 1990.
+  J.~M. Maestre, R.~R. Negenborn \emph{et~al.}
+  \newblock \emph{{D}istributed {M}odel {P}redictive {C}ontrol made easy}.\hskip 1em plus 0.5em minus 0.4em\relax
+  \newblock Springer, 2014, vol.~69.
 
@@
   % Followed by interesting articles. Keep the list short.
+
+\bibitem{VelardeEtAl2017a}
+P.~Velarde, J.~M. Maestre, H.~Ishii, and R.~R. Negenborn,
+\newblock ``Scenario-based
+defense mechanism for distributed model predictive control,''
+\newblock \emph{2017
+  IEEE 56th Annual Conference on Decision and Control (CDC)}.\hskip 1em plus
+  0.5em minus 0.4em\relax IEEE, Dec 2017, pp. 6171--6176.
 
@@
 \end{frame}
+\begin{frame}[plain]
+  \centering
+  \vfill
+       Questions?
+\vfill
+\begin{minipage}[t]{.45\linewidth}
+  \centering
+  Repository
+
+  \href{https://github.com/Accacio/SysTol-21}{https://github.com/Accacio/SysTol-21}
+
+  \includegraphics[width=2cm]{../img/qrRepo.png}
+\end{minipage}
+\begin{minipage}[t]{.5\linewidth}
+  \centering
+  Contact
+  \href{mailto:rafael-accacio.nogueira@centralesupelec.fr?subject=SysTol'21 Presentation}{rafael-accacio.nogueira@centralesupelec.fr}
+
+    \includegraphics[width=2cm]{../img/qrContact.png}
+\end{minipage}
+\end{frame}
 

### 2021-09-02 presentation/presentation.tex
colors and logos

@@
   \useinnertheme{circles}
+\definecolor{supelecRed}{RGB}{120,30,56}
+\definecolor{supelecPurple}{RGB}{104,95,115}
+%
+  % \setbeamercolor{palette primary}{bg=red!50!black!80}
+  \setbeamercolor{palette primary}{bg=supelecRed}
+  % \setbeamercolor{palette secondary}{bg=red!50!black!70}
+  \setbeamercolor{palette secondary}{bg=supelecRed}
+  \setbeamercolor{palette tertiary}{bg=gray!90!black!50}
+  % \setbeamercolor{palette tertiary}{bg=supelecPurple}
+  \setbeamercolor{palette quaternary}{bg=gray!90!black!90}
+  % \setbeamercolor{palette quaternary}{bg=supelecPurple}
+  % \setbeamercolor{block title}{bg=red!50!black!70}
+  \setbeamercolor{block title}{bg=supelecRed}
 
-  \setbeamercolor{palette primary}{bg=red!50!black!80}
-  \setbeamercolor{palette secondary}{bg=red!50!black!70}
-  \setbeamercolor{palette tertiary}{bg=gray!90!black!50}
-  \setbeamercolor{palette quaternary}{bg=gray!90!black!70}
-  \setbeamercolor{block title}{bg=red!50!black!70}
+  % \setbeamercolor{item}{fg=red!50!black!80}
+  \setbeamercolor{item}{fg=supelecRed}
+  % \setbeamercolor{section in toc}{fg=red!50!black!80}
+  \setbeamercolor{section in toc}{fg=supelecRed}
 
-  \setbeamercolor{item}{fg=red!50!black!80}
-  \setbeamercolor{section in toc}{fg=red!50!black!80}
-
-  \setbeamercolor{bibliography entry author}{fg=red!50!black!80}
-  \setbeamercolor{bibliography entry location}{fg=red!50!black!40}
+  % \setbeamercolor{bibliography entry author}{fg=red!50!black!80}
+  \setbeamercolor{bibliography entry author}{fg=supelecRed}
+  % \setbeamercolor{bibliography entry location}{fg=red!50!black!40}
+  \setbeamercolor{bibliography entry location}{fg=supelecRed!70}
 
@@
 % does not look nice, try deleting the line with the fontenc.
-
+\graphicspath{{../img/}}
 \usepackage{bm}
@@
 {R. A. Nogueira \and  R. Bourdais \and  H. Guéguen\\
-\texttt{\{rafael-accacio.nogueira,romain.bourdais,herve.gueguen\}\ at \ centralesupelec.fr}}
+\texttt{\{rafael-accacio.nogueira, romain.bourdais, herve.gueguen\}\\ at \\ centralesupelec.fr}}
 % - Give the names in the same order as the appear in the paper.
@@
     \centering
-    \includegraphics[width=2cm]{../img/logos/logo_IETR.png}
+    \includegraphics[width=2cm]{logos/logo_IETR.png}
   \end{minipage}
@@
     \vspace{10pt}
-    \includegraphics[width=1.5cm]{../img/qrPresentation.png}
+    \includegraphics[width=1.5cm]{qrPresentation.png}
+    % qrencode https://github.com/Accacio/SysTol-21/raw/main/presentation/presentation.pdf -o ~/git/SysTol21/img/qrPresentation.png
     \href{https://git.io/JEFGW}{https://git.io/JEFGW}
@@
     \vspace{10pt}
-    \includegraphics[width=2cm]{../img/logos/supelec.jpeg}
+    \includegraphics[width=2cm]{logos/supelec.jpeg}
   \end{minipage}
@@
 
-\logo{\includegraphics[height=.8cm]{../img/logos/supelec.jpeg}}
+\logo{\includegraphics[height=.8cm]{logos/supelec.jpeg}}
 
@@
 \begin{frame}
+  \begin{figure}[!t]
+    \centering
+    % inkscape -Dz flowchartAlg2.svg --export-latex -AflowchartAlg2.pdf
+    % \footnotesize
+    \def\svgwidth{.4\textwidth} \input{../img/flowchartAlg2.pdf_tex}
+    \caption{Scheme of DMPC using a \emph{coordinator} and $M$ agents.}\label{fig:schemeQuantity}
+  \end{figure}
+\end{frame}
+
+\begin{frame}
   \centering
@@
 \begin{frame}{Make Titles Informative.}
+  \begin{block}{te}
 
+  \end{block}
   You can create overlays\dots
@@
 \begin{frame}{Summary}
-  \begin{minipage}{.6\textwidth}
+  \pause
+  \begin{minipage}[t]{.45\textwidth}
     % Keep the summary *very short*.
@@
             Resource allocation based DMPC is vulnerable to attacks.
+            \pause
       \item
             Sub-problems structure has time invariant parameters.
+            \pause
       \item
             Attack can be estimated using these parameters.
+            \pause
     \end{enumerate}
-
+  \end{minipage}
+  \pause
     % The following outlook is optional.
-    \vskip0pt plus.5fill
+    % \vskip0pt plus.5fill
+  \begin{minipage}[t]{.45\textwidth}
     \begin{itemize}
-      \item
-            Outlook
+      \item Outlook
             \begin{itemize}
@@
 \end{frame}
+
 \begin{frame}[plain]
@@
   \begin{minipage}[t]{.45\linewidth}
+    \small
     \centering
     Repository
-
     \href{https://github.com/Accacio/SysTol-21}{https://github.com/Accacio/SysTol-21}
 
-  \includegraphics[width=2cm]{../img/qrRepo.png}
+    \includegraphics[width=2cm]{qrRepo.png}
   \end{minipage}
+  \hfill
   \begin{minipage}[t]{.5\linewidth}
+    \small
     \centering
@@
 
-    \includegraphics[width=2cm]{../img/qrContact.png}
+    \includegraphics[width=2cm]{qrContact.png}
   \end{minipage}

### 2021-09-03 presentation/presentation.tex
add flowchart

@@
 \usepackage[english]{babel}
+\usepackage{tikz}
+\usetikzlibrary{calc,shapes,positioning}
+\usetikzlibrary{overlay-beamer-styles}
 % or whatever
@@
   }
+
 \end{frame}
@@
 \begin{frame}
-  \begin{figure}[!t]
+  \begin{figure}[h]
     \centering
-    % inkscape -Dz flowchartAlg2.svg --export-latex -AflowchartAlg2.pdf
-    % \footnotesize
-    \def\svgwidth{.4\textwidth} \input{../img/flowchartAlg2.pdf_tex}
+  \scalebox{.6}{
+    \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
+      \draw[loosely dashed,
+      minimum width=2.5cm,
+      minimum height=1cm] (8cm,1cm) -- (8cm,-10cm);
+
+      \node[] at (5cm,0cm) {\Large Detection Phase};
+      \node[] at (11cm,0cm) {\Large Negotiation Phase};
+
+      \node[draw,
+      rounded rectangle,
+      fill=gray!90!black!50,
+      alt=<{2}>{fill=supelecRed!90,text=white},
+      minimum width=2.5cm,
+      minimum height=1cm] (block1) {Start};
+
+      \node[draw,
+      trapezium,
+      trapezium left angle = 65,
+      trapezium right angle = 115,
+      trapezium stretches,
+      align=center,
+      fill=supelecRed!10,
+      alt=<{3}>{fill=supelecRed!90,text=white},
+      below=of block1,
+      minimum width=3.5cm,
+      minimum height=1cm
+      ] (block2) { Coordinator sends \\random $\vec{\theta}_{i}^{(h)}$};
+
+      \node[draw,
+      trapezium,
+      trapezium left angle = 65,
+      trapezium right angle = 115,
+      trapezium stretches,
+      align=center,
+      fill=supelecRed!10,
+      alt=<{4}>{fill=supelecRed!90,text=white},
+      below=of block2,
+      minimum width=3.5cm,
+      minimum height=1cm
+      ] (block3) { Agents send \\ $\vec{\lambda}_{i}^{(h)}(\vec{\theta}_{i}^{(h)})$};
+
+      \node[draw,
+      trapezium,
+      trapezium left angle = 65,
+      trapezium right angle = 115,
+      trapezium stretches,
+      align=center,
+      below=of block3,
+      fill=supelecRed!10,
+      alt=<{5}>{fill=supelecRed!90,text=white},
+      minimum width=3.5cm,
+      minimum height=1cm
+      ] (block4) { Coordinator estimate parameters};
+
+      \node[draw,
+      diamond,
+      below=of block4,
+      minimum width=2.5cm,
+      fill=supelecRed!50,
+      alt=<{6}>{fill=supelecRed!90,text=white},
+      align=center,
+      inner sep=0] (block5) { Estimates\\ converge?};
+
+      \node[draw,
+      trapezium,
+      trapezium left angle = 65,
+      trapezium right angle = 115,
+      trapezium stretches,
+      align=center,
+      fill=supelecRed!10,
+      alt=<{7}>{fill=supelecRed!90,text=white},
+      right=1cm of block5,
+      minimum width=3.5cm,
+      minimum height=1cm
+      ] (block6) { Coordinator detects \\selfish agents};
+
+      \node[coordinate,right=6.cm of block2] (block12) {};
+
+      \node[draw,
+      trapezium,
+      trapezium left angle = 65,
+      trapezium right angle = 115,
+      trapezium stretches,
+      align=center,
+      right=of block12,
+      fill=supelecRed!10,
+      alt=<{8}>{fill=supelecRed!90,text=white},
+      minimum width=3.5cm,
+      minimum height=1cm
+      ] (block7) { Coordinator sends \\$\vec{\theta}_i^{(h)}$};
+      \node[draw,
+      trapezium,
+      trapezium left angle = 65,
+      trapezium right angle = 115,
+      trapezium stretches,
+      align=center,
+      fill=supelecRed!10,
+      alt=<{9}>{fill=supelecRed!90,text=white},
+      below=of block7,
+      minimum width=3.5cm,
+      minimum height=1cm
+      ] (block8) { Agents send \\$\vec{\lambda}_i(\vec{\theta}_{i}^{(h)})$};
+
+      \node[draw,
+      trapezium,
+      trapezium left angle = 65,
+      trapezium right angle = 115,
+      trapezium stretches,
+      align=center,
+      fill=supelecRed!10,
+      alt=<{10}>{fill=supelecRed!90,text=white},
+      below=of block8,
+      minimum width=3.5cm,
+      minimum height=1cm
+      ] (block9) { Coordinator updates \\allocation accordingly};
+
+      \node[draw,
+      diamond,
+      below=of block9,
+      minimum width=2.5cm,
+      fill=supelecRed!50,
+      alt=<{11}>{fill=supelecRed!90,text=white},
+      align=center,
+      inner sep=0] (block10) { Negotiation\\ converges?};
+
+      \node[draw,
+      rounded rectangle,
+      below=of block10,
+      fill=gray!90!black!50,
+      alt=<{12}>{fill=supelecRed!90,text=white},
+      minimum width=2.5cm,
+      minimum height=1cm,] (block11) { Apply first control};
+
+      \draw[-latex] (block1) edge (block2)
+      (block2) edge (block3)
+      (block3) edge (block4)
+      (block4) edge (block5);
+
+      \draw[-latex] (block7) edge (block8)
+      (block8) edge (block9)
+      (block9) edge (block10);
+
+      \draw[-latex] (block5) -- (block6)
+      node[pos=0.4,fill=white,inner sep=0]{Yes};
+
+      \draw[-latex] (block10) -- (block11)
+      node[pos=0.4,fill=white,inner sep=0]{Yes};
+
+      \draw[-latex] (block6) -| ($(block7.west) - (3cm,0)$) -- (block7.west);
+
+      \draw[-latex] (block10) -| ($(block7.east) + (1.5cm,0)$)
+      node[pos=0.25,fill=white,inner sep=0]{No} -- (block7.east);
+
+      \draw[-latex] (block5) -| ($(block2.west) - (1.5cm,0)$)
+      node[pos=0.25,fill=white,inner sep=0]{No} -- (block2.west);
+    \end{tikzpicture}
+    }
     \caption{Scheme of DMPC using a \emph{coordinator} and $M$ agents.}\label{fig:schemeQuantity}

### 2021-09-03 presentation/presentation.tex
correct space
add context images

@@
 
+\setbeamertemplate{caption}[numbered]
   % or whatever (possibly just delete it)
@@
 {R. A. Nogueira \and  R. Bourdais \and  H. Guéguen\\
-\texttt{\{rafael-accacio.nogueira, romain.bourdais, herve.gueguen\}\\ at \\ centralesupelec.fr}}
+\texttt{\{rafael-accacio.nogueira, romain.bourdais, herve.gueguen\} at  centralesupelec.fr}}
 % - Give the names in the same order as the appear in the paper.
@@
 
-% \begin{frame}[fragile]
-% \frametitle{An Algorithm For Finding Primes Numbers.}
-% \begin{semiverbatim}
-% \uncover<1->{\alert<0>{int main (void)}}
-% \uncover<1->{\alert<0>{\{}}
-% \uncover<1->{\alert<1>{ \alert<4>{std::}vector<bool> is_prime (100, true);}}
-% \uncover<1->{\alert<1>{ for (int i = 2; i < 100; i++)}}
-% \uncover<2->{\alert<2>{
-% if (is_prime[i])}}
-% \uncover<2->{\alert<0>{
-% \{}}
-% \uncover<3->{\alert<3>{
-% \alert<4>{std::}cout << i << " ";}}
-% \uncover<3->{\alert<3>{
-% for (int j = i; j < 100;}}
-% \uncover<3->{\alert<3>{
-% is_prime [j] = false, j+=i);}}
-% \uncover<2->{\alert<0>{
-% \}}}
-% \uncover<1->{\alert<0>{ return 0;}}
-% \uncover<1->{\alert<0>{\}}}
-% \end{semiverbatim}
-% \visible<4->{Note the use of \alert{\texttt{std::}}.}
+\begin{frame}{Context}
+  \begin{figure}
+    \includegraphics<1>[width=.6\textwidth]{the_city_nothing.pdf}%
+    \includegraphics<2>[width=.6\textwidth]{the_city_houses.pdf}%
+    \includegraphics<3>[width=.6\textwidth]{the_city_buildings.pdf}%
+    \includegraphics<4>[width=.6\textwidth]{the_city_cars.pdf}%
+  \end{figure}
+  \onslide<5->{
+  \begin{minipage}{.45\textwidth}
+    \includegraphics[width=\textwidth]{the_city_cars.pdf}%
+  \end{minipage}
+  \begin{minipage}{.5\textwidth}
+    \begin{itemize}
+      \item<6> Geographically distributed
+      \item<7> Coupled by constraints (energy)
+      \item<8> Optimization objectives
+            \begin{itemize}
+              \item Energy
+              \item User satisfaction
+              \item \dots
+            \end{itemize}
+      \item<9> Solution $\to$ Model Predictive Control
+    \end{itemize}
+  \end{minipage}
+  }
+\end{frame}
+
+\begin{frame}{Model Predictive Control}
+  Find control input sequence that optimizes an objective function
+
+\begin{equation*}
+\begin{matrix}
+\underset{\vec{u}(k:k+N_{p}-1|k)}{\mathrm{minimize}}&\resizebox{0.35\textwidth}{!}{$ \overbrace{\sum_{j=1}^{N_{p}}\|\vec{v}(k+j|k)\|^{2}_{Q}+\|\vec{u}(k+j-1|k)\|^{2}_{R}}^{\textstyle J_{G}(k)}$}\\
+\mathrm{subject~ to}&
+\left.\begin{matrix}
+    \vec{x}(k+1)=f(\vec{x}(k),\vec{u}(k)) \\
+    g_{i}(\vec{x}(k),\vec{u}(k))=0\\
+    h_{k}(\vec{x}(k),\vec{u}(k))\leq0\\
+\end{matrix}
+\right\}
+\begin{aligned}
+  &\forall i\in\{1,\dots,N_{p}\}\\
+  &\forall j\in\{1,\dots,N_{p}\}\\
+  &\forall k\in\{1,\dots,N_{p}\}
+\end{aligned}
+\end{matrix}
+\end{equation*}
+  Using
+\end{frame}
+
+% \begin{frame}
+%   \centering
+%   \begin{minipage}{.65\linewidth}
+%     \begin{algorithm}[H]
+%       \DontPrintSemicolon
+%       Coordinator initializes $\vec{\theta}^{(0)}$ \;
+%       $p:=0$\;
+%       \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
+%         Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;
+%         Coordinator updates allocations~\eqref{eq:thetaNegot}\;
+%         $p:=p+1$
+%       }
+%       \caption{Quantity decomposition based DMPC.}\label{alg:quantityAlg}
+%     \end{algorithm}
+%   \end{minipage}
 % \end{frame}
@@
 \begin{frame}
-\SetKwBlock{negotPhase}{ Negotiation Phase:}{}
-\SetKwBlock{detectPhase}{ Detection Phase:}{}
-\scalebox{.8}{  \begin{algorithm}[H]
-    \DontPrintSemicolon
-    \detectPhase{
-    $h:=0$\;
-    \Repeat{
-    $\|\eta_{i}^{h}-\eta^{h-1}\|\leq\epsilon$
-  }{
-    Coordinator sets random $\vec{\theta}_{i}^{(h+1)}$ \;
-    Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}^{(h)})$\;
-    Coordinator estimates $\widehat{\tilde{P}}_{i}(k)^{(h)}$ and $\widehat{\tilde{\vec{s}}}_{i}(k)^{(h)}$ \;
-    $h:=h+1$\;
+  \begin{figure}
+    \centering
+    \scalebox{.6}{
+      \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
+        \node[draw,
+        rounded rectangle,
+        fill=gray!90!black!50,
+        alt=<{2}>{fill=supelecRed!90,text=white},
+        minimum width=2.5cm,
+        minimum height=1cm] (block1) {Start};
+
+        \node[draw,
+        trapezium,
+        trapezium left angle = 65,
+        trapezium right angle = 115,
+        trapezium stretches,
+        align=center,
+        below=of block1,
+        fill=supelecRed!10,
+        alt=<{3}>{fill=supelecRed!90,text=white},
+        minimum width=3.5cm,
+        minimum height=1cm
+        ] (block7) { Coordinator sends \\$\vec{\theta}_i^{(h)}$};
+        \node[draw,
+        trapezium,
+        trapezium left angle = 65,
+        trapezium right angle = 115,
+        trapezium stretches,
+        align=center,
+        fill=supelecRed!10,
+        alt=<{4}>{fill=supelecRed!90,text=white},
+        below=of block7,
+        minimum width=3.5cm,
+        minimum height=1cm
+        ] (block8) { Agents send \\$\vec{\lambda}_i(\vec{\theta}_{i}^{(h)})$};
+
+        \node[draw,
+        trapezium,
+        trapezium left angle = 65,
+        trapezium right angle = 115,
+        trapezium stretches,
+        align=center,
+        fill=supelecRed!10,
+        alt=<{5}>{fill=supelecRed!90,text=white},
+        below=of block8,
+        minimum width=3.5cm,
+        minimum height=1cm
+        ] (block9) { Coordinator updates \\allocation};
+
+        \node[draw,
+        diamond,
+        below=of block9,
+        minimum width=2.5cm,
+        fill=supelecRed!50,
+        alt=<{6}>{fill=supelecRed!90,text=white},
+        align=center,
+        inner sep=0] (block10) { Negotiation\\ converges?};
+
+        \node[draw,
+        rounded rectangle,
+        below=of block10,
+        fill=gray!90!black!50,
+        alt=<{7}>{fill=supelecRed!90,text=white},
+        minimum width=2.5cm,
+        minimum height=1cm,] (block11) { Apply first control};
+
+        \draw[-latex] (block7) edge (block8)
+        (block1) edge (block7)
+        (block8) edge (block9)
+        (block9) edge (block10);
+
+        \draw[-latex] (block10) -- (block11)
+        node[pos=0.4,fill=white,inner sep=0]{Yes};
+
+        \draw[-latex] (block10) -| ($(block7.east) + (1.5cm,0)$)
+        node[pos=0.25,fill=white,inner sep=0]{No} -- (block7.east);
+
+      \end{tikzpicture}
     }
-    Coordinator computes $d_{i}$ using~\eqref{eq:2}\;
-  }
-    \negotPhase{
-    Coordinator initializes $\vec{\theta}^{(0)}$ \;
-    $p:=0$\;
+    \caption{Quantity decomposition based DMPC}\label{fig:quantityDecompDMPC}
+  \end{figure}
+\end{frame}
 
-    \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
-    Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;
+\begin{frame}{Outline}
+  \tableofcontents
+  % You might wish to add the option [pausesections]
+\end{frame}
 
-    Coordinator updates allocation~\eqref{eq:thetaNegot} using adequate versions of $\vec{\lambda}_{i}$ for each agent: $\vec{\lambda}_{i}^{\star}(\vec{\theta}\p)$, if $d_{i}=0$ and ${\vec{\lambda}_{i}}_{\mathrm{rec}}$, if ${d_{i}=1}$\;
-    $p:=p+1$
-  }}
-    \caption{Secure DMPC.}\label{alg:safeDMPC}
-  \end{algorithm}
-  }
+% Structuring a talk is a difficult task and the following structure
+% may not be suitable. Here are some rules that apply for this
+% solution:
 
+% - Exactly two or three sections (other than the summary).
+% - At *most* three subsections per section.
+% - Talk about 30s to 2min per frame. So there should be between about
+%   15 and 30 frames, all told.
+
+% - A conference audience is likely to know very little of what you
+%   are going to talk about. So *simplify*!
+% - In a 20min talk, getting the main ideas across is hard
+%   enough. Leave out details, even if it means being less precise than
+%   you think necessary.
+% - If you omit details that are vital to the proof/implementation,
+%   just say so once. Everybody will be happy with that.
+
+\section[Vulnerabilities in DMPC based on Resource Allocation]{Vulnerabilities in distributed MPC based on Resource Allocation}
+
+\subsection{The Basic Problem That We Studied}
+
+\begin{frame}{Make Titles Informative. Use Uppercase Letters.}{Subtitles are optional.}
+  \begin{itemize}
+  \item
+    Use \texttt{itemize} a lot.
+  \item
+    Use very short sentences or short phrases.
+  \end{itemize}
 \end{frame}
+
+\begin{frame}{Make Titles Informative.}
+  \begin{block}{te}
+
+  \end{block}
+  You can create overlays\dots
+  \begin{itemize}
+  \item using the \texttt{pause} command:
+    \begin{itemize}
+    \item
+      First item.
+      \pause
+    \item
+      Second item.
+    \end{itemize}
+  \item
+    using overlay specifications:
+    \begin{itemize}
+    \item<3->
+      First item.
+    \item<4->
+      Second item.
+    \end{itemize}
+  \item
+    using the general \texttt{uncover} command:
+    \begin{itemize}
+      \uncover<5->{\item
+        First item.}
+      \uncover<6->{\item
+        Second item.}
+    \end{itemize}
+  \end{itemize}
+\end{frame}
+
+\subsection{Previous Work}
+
+\begin{frame}{Make Titles Informative.}
+\end{frame}
+
+\section{Securing the DMPC}
+% \begin{frame}
+% \SetKwBlock{negotPhase}{ Negotiation Phase:}{}
+% \SetKwBlock{detectPhase}{ Detection Phase:}{}
+% \scalebox{.8}{  \begin{algorithm}[H]
+%     \DontPrintSemicolon
+%     \detectPhase{
+%     $h:=0$\;
+%     \Repeat{
+%     $\|\eta_{i}^{h}-\eta^{h-1}\|\leq\epsilon$
+%   }{
+%     Coordinator sets random $\vec{\theta}_{i}^{(h+1)}$ \;
+%     Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}^{(h)})$\;
+%     Coordinator estimates $\widehat{\tilde{P}}_{i}(k)^{(h)}$ and $\widehat{\tilde{\vec{s}}}_{i}(k)^{(h)}$ \;
+%     $h:=h+1$\;
+%   }
+%     Coordinator computes $d_{i}$ using~\eqref{eq:2}\;
+%   }
+%     \negotPhase{
+%     Coordinator initializes $\vec{\theta}^{(0)}$ \;
+%     $p:=0$\;
+
+%     \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
+%     Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;
+
+%     Coordinator updates allocation~\eqref{eq:thetaNegot} using adequate versions of $\vec{\lambda}_{i}$ for each agent: $\vec{\lambda}_{i}^{\star}(\vec{\theta}\p)$, if $d_{i}=0$ and ${\vec{\lambda}_{i}}_{\mathrm{rec}}$, if ${d_{i}=1}$\;
+%     $p:=p+1$
+%   }}
+%     \caption{Secure DMPC.}\label{alg:safeDMPC}
+%   \end{algorithm}
+%   }
+% \end{frame}
 
@@
     }
-    \caption{Scheme of DMPC using a \emph{coordinator} and $M$ agents.}\label{fig:schemeQuantity}
+    \caption{Secure DMPC}\label{fig:secureDMPC}
   \end{figure}
-\end{frame}
-
-\begin{frame}
-  \centering
-  \begin{minipage}{.65\linewidth}
-    \begin{algorithm}[H]
-      \DontPrintSemicolon
-      Coordinator initializes $\vec{\theta}^{(0)}$ \;
-      $p:=0$\;
-      \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
-        Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;
-        Coordinator updates allocations~\eqref{eq:thetaNegot}\;
-        $p:=p+1$
-      }
-      \caption{Quantity decomposition based DMPC.}\label{alg:quantityAlg}
-    \end{algorithm}
-  \end{minipage}
-\end{frame}
-
-\begin{frame}{Outline}
-  \tableofcontents
-  % You might wish to add the option [pausesections]
-\end{frame}
-
-% Structuring a talk is a difficult task and the following structure
-% may not be suitable. Here are some rules that apply for this
-% solution:
-
-% - Exactly two or three sections (other than the summary).
-% - At *most* three subsections per section.
-% - Talk about 30s to 2min per frame. So there should be between about
-%   15 and 30 frames, all told.
-
-% - A conference audience is likely to know very little of what you
-%   are going to talk about. So *simplify*!
-% - In a 20min talk, getting the main ideas across is hard
-%   enough. Leave out details, even if it means being less precise than
-%   you think necessary.
-% - If you omit details that are vital to the proof/implementation,
-%   just say so once. Everybody will be happy with that.
-
-\section{Motivation}
-
-\subsection{The Basic Problem That We Studied}
-
-\begin{frame}{Make Titles Informative. Use Uppercase Letters.}{Subtitles are optional.}
-  % - A title should summarize the slide in an understandable fashion
-  %   for anyone how does not follow everything on the slide itself.
-
-  \begin{itemize}
-  \item
-    Use \texttt{itemize} a lot.
-  \item
-    Use very short sentences or short phrases.
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Make Titles Informative.}
-  \begin{block}{te}
-
-  \end{block}
-  You can create overlays\dots
-  \begin{itemize}
-  \item using the \texttt{pause} command:
-    \begin{itemize}
-    \item
-      First item.
-      \pause
-    \item
-      Second item.
-    \end{itemize}
-  \item
-    using overlay specifications:
-    \begin{itemize}
-    \item<3->
-      First item.
-    \item<4->
-      Second item.
-    \end{itemize}
-  \item
-    using the general \texttt{uncover} command:
-    \begin{itemize}
-      \uncover<5->{\item
-        First item.}
-      \uncover<6->{\item
-        Second item.}
-    \end{itemize}
-  \end{itemize}
-\end{frame}
-
-\subsection{Previous Work}
-
-\begin{frame}{Make Titles Informative.}
-\end{frame}
-
-\begin{frame}{Make Titles Informative.}
 \end{frame}
@@
 
-\begin{frame}{Make Titles Informative.}
-\end{frame}
-
-\begin{frame}{Make Titles Informative.}
-\end{frame}
-
 \subsection{Basic Ideas for Proofs/Implementation}
-
-\begin{frame}{Make Titles Informative.}
-\end{frame}
-
-\begin{frame}{Make Titles Informative.}
-\end{frame}
 
@@
       \item
-            Attack can be estimated using these parameters.
-            \pause
+            Attacks can be detected using these parameters.
     \end{enumerate}
@@
       \item Outlook
+            \pause
             \begin{itemize}
@@
                     Inequality Constraints yield Hybrid behavior
+                    \pause
               \item
@@
 
-\nocite{VelardeEtAl2017a}
+% \nocite{VelardeEtAl2017a}
 % All of the following is optional and typically not needed.
@@
 
+\appendix
 \begin{frame}[allowframebreaks]
@@
 \end{frame}
-
 \begin{frame}[plain]

### 2021-09-06 presentation/presentation.tex
mpc graphic

@@
   \end{figure}
-  \onslide<5->{
+  \only<5->{
   \begin{minipage}{.45\textwidth}
@@
 \begin{frame}{Model Predictive Control}
-  Find control input sequence that optimizes an objective function
-
-\begin{equation*}
+  Objective: Find control input sequence that optimizes an objective function
+  \only<1-5>{\begin{equation*}
     \begin{matrix}
-\underset{\vec{u}(k:k+N_{p}-1|k)}{\mathrm{minimize}}&\resizebox{0.35\textwidth}{!}{$ \overbrace{\sum_{j=1}^{N_{p}}\|\vec{v}(k+j|k)\|^{2}_{Q}+\|\vec{u}(k+j-1|k)\|^{2}_{R}}^{\textstyle J_{G}(k)}$}\\
+      \underset{\vec{u}(k:k+\alert<3>{N_{p}}-1|k)}{\mathrm{optimize}}&\alert<2>{J(\vec{x}(k),\vec{u}(k))}\\
       \mathrm{subject~ to}&
-\left.\begin{matrix}
-    \vec{x}(k+1)=f(\vec{x}(k),\vec{u}(k)) \\
-    g_{i}(\vec{x}(k),\vec{u}(k))=0\\
-    h_{k}(\vec{x}(k),\vec{u}(k))\leq0\\
+      \left.
+        \begin{matrix}
+          \alert<4>{\vec{x}(\xi+1)=f(\vec{x}(\xi),\vec{u}(\xi))}\\
+          \alert<5>{g_{i}(\vec{x}(\xi),\vec{u}(\xi))\leq0}\\
+          \alert<5>{h_{j}(\vec{x}(\xi),\vec{u}(\xi))=0}\\
         \end{matrix}
@@
       \begin{aligned}
-  &\forall i\in\{1,\dots,N_{p}\}\\
-  &\forall j\in\{1,\dots,N_{p}\}\\
-  &\forall k\in\{1,\dots,N_{p}\}
+        &\forall \xi\in\{1,\dots,\alert<3>{N_{p}}\}\\
+        &\forall i\in\{1,\dots,m\}\\
+        &\forall j\in\{1,\dots,p\}
+      \end{aligned}
+    \end{matrix}
+  \end{equation*}}%
+\only<6->{
+  \begin{equation*}
+    \begin{matrix}
+      \underset{\vec{u}(k:k+N_{p}-1|k)}{\mathrm{minimize}}&  \sum_{j=1}^{N_{p}}\|\vec{v}(k+j|k)\|^{2}_{Q}+\|\vec{u}(k+j-1|k)\|^{2}_{R}\\
+      \mathrm{subject~ to}&
+      \left.
+        \begin{matrix}
+          \vec{x}(\xi+1)=f(\vec{x}(\xi),\vec{u}(\xi)) \\
+          g_{i}(\vec{x}(\xi),\vec{u}(\xi))\leq0\\
+          h_{j}(\vec{x}(\xi),\vec{u}(\xi))=0\\
+        \end{matrix}
+      \right\}
+      \begin{aligned}
+        &\forall \xi\in\{1,\dots,N_{p}\}\\
+        &\forall i\in\{1,\dots,m\}\\
+        &\forall j\in\{1,\dots,p\}
       \end{aligned}
@@
   \end{equation*}
-  Using
+  }%
+\end{frame}
+
+\begin{frame}{Model Predictive Control}
+  Find sequence, \pause apply first control, \pause rinse repeat \pause $\to$ Receding Horizon
+
+  \begin{figure}
+    \centering
+    \foreach \i in {1,...,10}{\includegraphics<\i>[width=.5\textwidth]{mpc\i.pdf}%
+    }
+  \end{figure}
+\end{frame}
+
+\begin{frame}
+  \begin{itemize}
+    \item Problem: Complexity depends on $N_{p},m,p$ and sizes of $\vec{x}$ and $\vec{u}$
+    \item Solution: Divide and Conquer
+  \end{itemize}
 \end{frame}

### 2021-09-06 script/mpcRun.m

@@ -1,0 +1,113 @@
+clear
+clc
+simK=10;
+Te=0.5;
+n=5;
+
+% options = optimset('Display', 'off')
+opts = optimoptions('quadprog', 'MaxIter', 200, 'Display','off');
+
+X0(:,1) = [18.3 3.0]';
+
+umin = [0 ];
+umax = [2 ];
+
+Rf=[5];
+Ri=[2.5];
+Ro=[0.5];
+Cres=[5];
+Cs=[8];
+
+Wt(:,:,1) = [20*ones(1,floor(simK/2)) 21*ones(1,simK-floor(simK/2))];
+
+A=@(Cres,Cs,Rf,Ri,Ro) [-1/(Cres*Rf)-1/(Cres*Ri) 1/(Cres*Ri); 1/(Cs*Ri) -1/(Cs*Ro)-1/(Cs*Ri)];
+B=@(Cres,Cs,Rf,Ro) [10/Cres 1/(Cres*Rf); 0 1/(Cs*Ro)];
+Bp=@(Cres,Cs,Rf,Ro) [10/Cres; 0];
+C=[1 0]; D=[0 0];
+
+psys = c2d(ss(A(Cres,Cs,Rf,Ri,Ro),Bp(Cres,Cs,Rf,Ro),C,D(:,1)),Te);
+sys.A = psys.A; sys.B = psys.B; sys.C = psys.C; sys.D = psys.D;
+K=1;
+xt(:,K) = X0;
+Wt = Wt(:,:);
+sys.umin = umin(:);  sys.umax = umax(:);
+
+s= size(sys.A,1);   % number of states  of each subsystem
+o= size(sys.C,1); % number of outputs of each subsystem
+c= size(sys.B,2); % number of inputs  of each subsystem
+Q(:,:)=eye(n*size(sys.C,1)); % no x no
+R(:,:)=eye(n*size(sys.B,2)); % nc x nc
+
+paren = @(x, varargin) x(varargin{:}); %
+                                       % apply index in created elements
+curly = @(x, varargin) x{varargin{:}}; %
+
+getMmat=@(A,C,n) ...
+ cell2mat( ...
+    (repmat(mat2cell(C,1),1,n) .* ...
+     (repmat(mat2cell(A,size(A,2)),1,n).^num2cell(1:n)) ...
+    )'  ...
+  );
+
+getCmat=@(A, B, C, n) ...
+    cell2mat( ...
+      paren( ...
[…]

### 2021-09-07 img/mpcState1.tex
tex plot

% This file was created by matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.47000,0.12000,0.22000}%
%
\begin{tikzpicture}

\begin{axis}[%
width=0.959\fwidth,
height=\fheight,
at={(0\fwidth,0\fheight)},
scale only axis,
xmin=1,
xmax=10,
ymin=18,
ymax=22,
ylabel style={font=\color{white!15!black}},
ylabel={$\text{Temperature (}^\text{o}\text{C)}$},
axis background/.style={fill=white},
title style={font=\bfseries},
title={Temperature in Room},
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black}
]
\addplot[const plot, color=gray, line width=1.5pt] table[row sep=crcr] {%
1	20\\
2	20\\
3	20\\
4	20\\
5	20\\
6	21\\
7	21\\
8	21\\
9	21\\
10	21\\
};
\addlegendentry{Setpoint}

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
2	19.1809073117312\\
3	19.591726028418\\
4	19.7017653509018\\
5	19.6096822707726\\
6	19.2336793296855\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
2	18\\
2	22\\
6	22\\
6	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

### 2021-09-07 img/mpcState10.tex
tex plot

--- 2021-09-07 img/mpcState1.tex
@@
 1	18.3\\
+2	19.2922432972485\\
+3	19.7421558473231\\
+4	19.9080020336521\\
+5	19.9691994260194\\
+6	19.991835840366\\
+7	20.6315685911097\\
+8	20.8673492565163\\
+9	20.9543208818143\\
+10	20.9864637751245\\
 };
@@
   table[row sep=crcr]{%
-2	19.1809073117312\\
-3	19.591726028418\\
-4	19.7017653509018\\
-5	19.6096822707726\\
-6	19.2336793296855\\
+11	20.9349764035864\\
+12	20.8913786496969\\
+13	20.8170082544264\\
+14	20.6458633361213\\
+15	20.225626806513\\
 };
@@
 x	y\\
-2	18\\
-2	22\\
-6	22\\
-6	18\\
+11	18\\
+11	22\\
+15	22\\
+15	18\\
 }--cycle;

### 2021-09-07 img/mpcState2.tex
tex plot

--- 2021-09-07 img/mpcState1.tex
@@
 1	18.3\\
+2	19.2922432972485\\
 };
@@
   table[row sep=crcr]{%
-2	19.1809073117312\\
-3	19.591726028418\\
-4	19.7017653509018\\
-5	19.6096822707726\\
-6	19.2336793296855\\
+3	19.6586714912936\\
+4	19.7837827178459\\
+5	19.7795571241486\\
+6	19.6425574643411\\
+7	19.250864938813\\
 };
@@
 x	y\\
-2	18\\
-2	22\\
-6	22\\
-6	18\\
+3	18\\
+3	22\\
+7	22\\
+7	18\\
 }--cycle;

### 2021-09-07 img/mpcState3.tex
tex plot

--- 2021-09-07 img/mpcState1.tex
@@
 1	18.3\\
+2	19.2922432972485\\
+3	19.7421558473231\\
 };
@@
   table[row sep=crcr]{%
-2	19.1809073117312\\
-3	19.591726028418\\
-4	19.7017653509018\\
-5	19.6096822707726\\
-6	19.2336793296855\\
+4	19.8393846180052\\
+5	19.8565364414247\\
+6	19.8091433705635\\
+7	19.6552196518173\\
+8	19.2577473135317\\
 };
@@
 x	y\\
-2	18\\
-2	22\\
-6	22\\
-6	18\\
+4	18\\
+4	22\\
+8	22\\
+8	18\\
 }--cycle;

### 2021-09-07 img/mpcState4.tex
tex plot

--- 2021-09-07 img/mpcState2.tex
@@
 2	19.2922432972485\\
+3	19.7421558473231\\
+4	19.9080020336521\\
 };
@@
   table[row sep=crcr]{%
-3	19.6586714912936\\
-4	19.7837827178459\\
-5	19.7795571241486\\
-6	19.6425574643411\\
-7	19.250864938813\\
+5	19.9061064592983\\
+6	19.8834999029294\\
+7	19.8202183303531\\
+8	19.6601073221883\\
+9	19.2606457774807\\
 };
@@
 x	y\\
-3	18\\
-3	22\\
-7	22\\
-7	18\\
+5	18\\
+5	22\\
+9	22\\
+9	18\\
 }--cycle;

### 2021-09-07 img/mpcState5.tex
tex plot

--- 2021-09-07 img/mpcState2.tex
@@
 2	19.2922432972485\\
+3	19.7421558473231\\
+4	19.9080020336521\\
+5	19.9691994260194\\
 };
@@
   table[row sep=crcr]{%
-3	19.6586714912936\\
-4	19.7837827178459\\
-5	19.7795571241486\\
-6	19.6425574643411\\
-7	19.250864938813\\
+6	19.930819433945\\
+7	19.8935742358252\\
+8	19.8244502967148\\
+9	19.6621002443578\\
+10	19.2620262577271\\
 };
@@
 x	y\\
-3	18\\
-3	22\\
-7	22\\
-7	18\\
+6	18\\
+6	22\\
+10	22\\
+10	18\\
 }--cycle;

### 2021-09-07 img/mpcState6.tex
tex plot

--- 2021-09-07 img/mpcState3.tex
@@
 3	19.7421558473231\\
+4	19.9080020336521\\
+5	19.9691994260194\\
+6	19.991835840366\\
 };
@@
   table[row sep=crcr]{%
-4	19.8393846180052\\
-5	19.8565364414247\\
-6	19.8091433705635\\
-7	19.6552196518173\\
-8	19.2577473135317\\
+7	20.5351500004865\\
+8	20.7301076659588\\
+9	20.7510970131778\\
+10	20.6172133181397\\
+11	20.2093321462984\\
 };
@@
 x	y\\
-4	18\\
-4	22\\
-8	22\\
-8	18\\
+7	18\\
+7	22\\
+11	22\\
+11	18\\
 }--cycle;

### 2021-09-07 img/mpcState7.tex
tex plot

--- 2021-09-07 img/mpcState4.tex
@@
 4	19.9080020336521\\
+5	19.9691994260194\\
+6	19.991835840366\\
+7	20.6315685911097\\
 };
@@
   table[row sep=crcr]{%
-5	19.9061064592983\\
-6	19.8834999029294\\
-7	19.8202183303531\\
-8	19.6601073221883\\
-9	19.2606457774807\\
+8	20.7920443673713\\
+9	20.8334722976929\\
+10	20.7930677686674\\
+11	20.6350899301155\\
+12	20.2189083589457\\
 };
@@
 x	y\\
-5	18\\
-5	22\\
-9	22\\
-9	18\\
+8	18\\
+8	22\\
+12	22\\
+12	18\\
 }--cycle;

### 2021-09-07 img/mpcState8.tex
tex plot

--- 2021-09-07 img/mpcState5.tex
@@
 5	19.9691994260194\\
+6	19.991835840366\\
+7	20.6315685911097\\
+8	20.8673492565163\\
 };
@@
   table[row sep=crcr]{%
-6	19.930819433945\\
-7	19.8935742358252\\
-8	19.8244502967148\\
-9	19.6621002443578\\
-10	19.2620262577271\\
+9	20.8868479256373\\
+10	20.8717333373315\\
+11	20.8087284948109\\
+12	20.6419287074761\\
+13	20.2228485328721\\
 };
@@
 x	y\\
-6	18\\
-6	22\\
-10	22\\
-10	18\\
+9	18\\
+9	22\\
+13	22\\
+13	18\\
 }--cycle;

### 2021-09-07 img/mpcState9.tex
tex plot

--- 2021-09-07 img/mpcState6.tex
@@
 6	19.991835840366\\
+7	20.6315685911097\\
+8	20.8673492565163\\
+9	20.9543208818143\\
 };
@@
   table[row sep=crcr]{%
-7	20.5351500004865\\
-8	20.7301076659588\\
-9	20.7510970131778\\
-10	20.6172133181397\\
-11	20.2093321462984\\
+10	20.9219229812564\\
+11	20.8859883781932\\
+12	20.8146703364917\\
+13	20.6446665111643\\
+14	20.2246553047596\\
 };
@@
 x	y\\
-7	18\\
-7	22\\
-11	22\\
-11	18\\
+10	18\\
+10	22\\
+14	22\\
+14	18\\
 }--cycle;

### 2021-09-07 presentation/presentation.tex
tex plot

@@
 \usetikzlibrary{overlay-beamer-styles}
+\usepackage{pgfplots}
+ \usetikzlibrary{plotmarks}
+  \usetikzlibrary{arrows.meta}
+  \usepgfplotslibrary{patchplots}
+  \usepackage{grffile}
 % or whatever
@@
 
+\newlength\fheight
+\newlength\fwidth
+\setlength\fwidth{.35\textwidth}
+\setlength\fheight{.8\fwidth}
+
 \begin{frame}{Model Predictive Control}
-  Find sequence, \pause apply first control, \pause rinse repeat \pause $\to$ Receding Horizon
+  \only<1->{Find optimal control sequence}%
+  \only<2->{, apply first element}%
+  \only<3->{, rinse repeat}%
+  \only<4->{ $\to$ Receding Horizon}%
 
@@
     \centering
-    \foreach \i in {1,...,10}{\includegraphics<\i>[width=.5\textwidth]{mpc\i.pdf}%
+    \foreach \i in {1,...,10}{%
+      % \includegraphics<\i>[width=.5\textwidth]{mpc\i.pdf}%
+      \only<{\i}>{\input{../img/mpcState\i.tex}}%
+      \only<{\i}>{\input{../img/mpcControl\i.tex}}%
     }
@@
 
-\begin{frame}
+\begin{frame}[label=current]
   \begin{itemize}
@@
   \end{itemize}
+  \vfill
+  \begin{figure}
+    \centering
+    \only<1>{
+    \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
+      \node[draw,
+      rectangle,
+      trapezium stretches,
+      align=center,
+      fill=supelecRed!10,
+      alt=<{3}>{fill=supelecRed!90,text=white},
+      minimum width=3.5cm,
+      minimum height=4cm
+      ] (block1) {MPC};
+    \end{tikzpicture}
+    }%
+    \only<2>{
+      \tikzset{mpcSmall/.style={
+      rectangle,
+      align=center,
+      fill=supelecRed!10,
+      minimum width=2.cm,
+      minimum height=.5cm},
+    coordinator/.style={
+    rectangle,
+    trapezium stretches,
+    align=center,
+    fill=supelecRed!10,
+    minimum width=1cm,
+    minimum height=4cm
+    }}
+  \begin{tikzpicture}[font=\small,thick,node distance=.35cm and .5cm]
+
+    \node[draw,
+    mpcSmall
+    ] (block1) {MPC};
+
+    \node[draw,
+    mpcSmall,
+    below=of block1,
+    ] (block2) {MPC};
+
+    \node[draw,
+    mpcSmall,
+    below=of block2,
+    ] (block3) {MPC};
+
+    \node[draw,
+    mpcSmall,
+    fill=none,
+    draw=white,
+    below=of block3,
+    ] (block4) {\vdots};
+    \node[draw,
+    mpcSmall,
+    below=of block4,
+    ] (block5) {MPC};
+
+    \node[draw,
+    coordinator,
+    right=of block3,
+    ] (coordinator) {\rotatebox{90}{Coordinator}};
+
+\draw (block2) -- (coordinator);
+\draw (block3) -- (coordinator);
+
+  \end{tikzpicture}
+}%
+
+\end{figure}
 \end{frame}

### 2021-09-07 script/mpcRun.m

@@ -1,4 +1,4 @@
-clear
+close all; clear
 clc
 simK=10;
 Te=0.5;
@@ -6,6 +6,7 @@ n=5;
 
 % options = optimset('Display', 'off')
 opts = optimoptions('quadprog', 'MaxIter', 200, 'Display','off');
+% opts = optimoptions('quadprog', 'Display','off');
 
 X0(:,1) = [18.3 3.0]';
 
@@ -18,7 +19,7 @@ Ro=[0.5];
 Cres=[5];
 Cs=[8];
 
-Wt(:,:,1) = [20*ones(1,floor(simK/2)) 21*ones(1,simK-floor(simK/2))];
+Wt(:,:,1) = [20*ones(1,5) 21*ones(1,5)];
 
 A=@(Cres,Cs,Rf,Ri,Ro) [-1/(Cres*Rf)-1/(Cres*Ri) 1/(Cres*Ri); 1/(Cs*Ri) -1/(Cs*Ro)-1/(Cs*Ri)];
 B=@(Cres,Cs,Rf,Ro) [10/Cres 1/(Cres*Rf); 0 1/(Cs*Ro)];
@@ -84,11 +85,15 @@ end
 
 %%
 for K=1:simK
-    stairs(1:simK,Wt,'r')
+%   subplot(2,1,1);
+    figure
+    stairs(1:simK,Wt,'LineWidth',1.5,'Color',[0.5 0.5 0.5])
     hold on
-    plot(1:K,xt(1,1:K),'b*')
-    stairs(K:K+n,[xt(1,K) xtPred(:,K)'],'k--')
+    plot(1:K,xt(1,1:K),'^','Color',[0.47 0.12 0.22],'MarkerFaceColor',[0.47 0.12 0.22])
+    plot(K+1:K+n,[xtPred(:,K)'],'^','LineWidth',1,'Color',([1 1 1]+[0.47 0.12 0.22])/2)
+    patch([K+1 K+1 K+n K+n],[18 22 22 18],[.47 .12 .22],'FaceAlpha',.1,'EdgeColor','none')
     hold off
+    ylabel('Temperature (^oC)')
     xlim([1 simK])
     ylim([18 22])
     set(gcf, 'PaperPosition', [0 0 8 7])
@@ -96,18 +101,37 @@ for K=1:simK
     set(gca,'FontSize',18)
     set(gca,'FontName','cmr18')
     set(gcf, 'PaperSize', [8 7])
[…]

### 2021-09-09 presentation/presentation.tex
update presentation

@@
 \documentclass[aspectratio=169]{beamer}
+% \includeonlyframes{current}
 
@@
   \useinnertheme{circles}
+  \usefonttheme[onlymath]{serif}
 \definecolor{supelecRed}{RGB}{120,30,56}
@@
   \setbeamercolor{block title}{bg=supelecRed}
+  \setbeamercolor{block title example}{bg=gray!90!black!90}
+  \setbeamercolor{block title example}{bg=gray!90!black!90}
 
@@
 \usepackage{pgfplots}
+\usepackage{amssymb}
  \usetikzlibrary{plotmarks}
@@
   \usepackage{grffile}
+\usepackage{booktabs}       % filenames
 % or whatever
@@
 \newcommand{\enstq}[2]{\{#1\mathrel{}\mid\mathrel{}#2\}}
+
+\newtheorem{assumption}{Assumption}%[numberby]
 
@@
 % the beginning of each subsection:
-\AtBeginSubsection[]
+\AtBeginSection[]
 {
   \begin{frame}<beamer>{Outline}
-    \tableofcontents[currentsection,currentsubsection]
+    \tableofcontents[currentsection,subsectionstyle=show/show/shaded]
   \end{frame}
@@
 
+% \begin{frame}{Context}
+%   \begin{figure}
+%     \includegraphics<1>[width=.6\textwidth]{the_city_nothing.pdf}%
+%     \includegraphics<2>[width=.6\textwidth]{the_city_houses.pdf}%
+%     \includegraphics<3>[width=.6\textwidth]{the_city_buildings.pdf}%
+%     \includegraphics<4>[width=.6\textwidth]{the_city_cars.pdf}%
+%   \end{figure}
+%   \only<5->{
+%   \begin{minipage}{.45\textwidth}
+%     \includegraphics[width=\textwidth]{the_city_cars.pdf}%
+%   \end{minipage}
+%   \begin{minipage}{.5\textwidth}
+%     \begin{itemize}
+%       \item<6> Geographically distributed
+%       \item<7> Coupled by constraints (energy)
+%       \item<8> Optimization objectives
+%             \begin{itemize}
+%               \item Energy
+%               \item User satisfaction
+%               \item \dots
+%             \end{itemize}
+%       \item<9> Solution $\to$ Model Predictive Control
+%     \end{itemize}
+%   \end{minipage}
+%   }
+% \end{frame}
+
 \begin{frame}{Context}
-  \begin{figure}
-    \includegraphics<1>[width=.6\textwidth]{the_city_nothing.pdf}%
-    \includegraphics<2>[width=.6\textwidth]{the_city_houses.pdf}%
-    \includegraphics<3>[width=.6\textwidth]{the_city_buildings.pdf}%
-    \includegraphics<4>[width=.6\textwidth]{the_city_cars.pdf}%
-  \end{figure}
-  \only<5->{
+  \centering
+  Smart City\\
   \begin{minipage}{.45\textwidth}
@@
   \end{minipage}
+  \only<2-5>{
+  \begin{minipage}{.5\textwidth}
+    \begin{itemize}
+      \item<2> Energy Distribution System
+      \item<3> Traffic management
+      \item<4> Heat distribution
+      \item<5> Water distribution
+      \item<5>[] \dots
+    \end{itemize}
+  \end{minipage}
+  }
+\only<6->{
   \begin{minipage}{.5\textwidth}
@@
     \centering
-    \foreach \i in {1,...,10}{%
+    \foreach \i in {1,...,4}{%
       % \includegraphics<\i>[width=.5\textwidth]{mpc\i.pdf}%
@@
 
-\begin{frame}[label=current]
+\begin{frame}{Distributed Model Predictive Control}
   \begin{itemize}
-    \item Problem: Complexity depends on $N_{p},m,p$ and sizes of $\vec{x}$ and $\vec{u}$
-    \item Solution: Divide and Conquer
+    \item<1> Problem: Complexity depends on $N_{p},m,p$ and sizes of $\vec{x}$ and $\vec{u}$
+    \item<2> Solution: Divide and Conquer
   \end{itemize}
   \vfill
+  \centering
+  \begin{minipage}[c]{.45\linewidth}
     \begin{figure}
@@
       \only<2>{
-      \tikzset{mpcSmall/.style={
+        \begin{tikzpicture}[font=\small,thick,node distance=.2cm and .5cm,
+          mpcSmall/.style={
             rectangle,
@@
             minimum width=2.cm,
-      minimum height=.5cm},
+            minimum height=.4cm},
           coordinator/.style={
             rectangle,
-    trapezium stretches,
             align=center,
@@
             minimum height=4cm
-    }}
-  \begin{tikzpicture}[font=\small,thick,node distance=.35cm and .5cm]
+          } ]
 
@@
           mpcSmall
-    ] (block1) {MPC};
-
-    \node[draw,
-    mpcSmall,
-    below=of block1,
-    ] (block2) {MPC};
-
-    \node[draw,
-    mpcSmall,
-    below=of block2,
-    ] (block3) {MPC};
+          ] (block1) {MPC M};
 
@@
           draw=white,
+          below=of block1,
+          ] (block2) {\vdots};
+
+          \node[draw,
+          mpcSmall,
+          below=of block2,
+          ] (block3) {MPC 3};
+
+          \node[draw,
+          mpcSmall,
           below=of block3,
-    ] (block4) {\vdots};
+          ] (block4) {MPC 2};
           \node[draw,
@@
           below=of block4,
-    ] (block5) {MPC};
+          ] (block5) {MPC 1};
 
@@
 
-\draw (block2) -- (coordinator);
-\draw (block3) -- (coordinator);
+          \draw[latex-latex] (block1.east) -- (block1.east -| coordinator.west);
+          \draw[latex-latex] (block3.east) -- (block3.east -| coordinator.west);
+          \draw[latex-latex] (block4.east) -- (block4.east -| coordinator.west);
+          \draw[latex-latex] (block5.east) -- (block5.east -| coordinator.west);
 
@@
       }%
-
     \end{figure}
+  \end{minipage}
 \end{frame}
 
+\begin{frame}{Distributed Model Predictive Control}{Quantity Decomposition | Resource Allocation}
+  \centering
+  \only<4>{
+    \begin{minipage}[t]{.3\linewidth}
+      \begin{figure}[!t]
+        \scalebox{.7}{\footnotesize \def\svgwidth{8cm} \input{../img/diagQuantMod.pdf_tex}}
+      \end{figure}
+    \end{minipage}
+    \hfill
+  }
+  \only<1>{
+    \begin{equation*}
+      \scalebox{1}{
+        $\displaystyle
+        \begin{matrix}
+          \underset{\vec{u}_i(k:k+N_{p}-1|k)}{\mathrm{minimize}}&\overbrace{\sum\limits^{M}_{i=1} \overbrace{\sum_{j=1}^{N_{p}}\|\vec{v}_i(k+j|k)\|^{2}_{Q_i}+\|\vec{u}_i(k+j-1|k)\|^{2}_{R_i}}^{\textstyle J_{i}(k)}}^{\textstyle J_{G}(k)}\\
+          \mathrm{subject~ to}&
+          \left.
+            \begin{matrix}
+              \vec{x}_{i}(k+1)=A_{i}\vec{x}_{i}(k) + B_{i}\vec{u}_{i}(k)\\
+              \sum^{M}_{i=1}\Gamma_{i}\vec{u}_{i}(k)=\vec{u}_{\mathrm{\max}}\\
+            \end{matrix}
+          \right\}
+          \begin{aligned}
+            &\forall i\in\{1,\dots,M\}\\
+            &\forall j\in\{1,\dots,N_{p}\}
+          \end{aligned}
+        \end{matrix}
+        $}
+    \end{equation*}
+  }
+  \only<2->{
+    \begin{minipage}[t]{.6\linewidth}
+      \centering
+      \begin{equation*}
+        \scalebox{.8}{
+          $\displaystyle
+          \left.
+            \small
+            \begin{aligned}
+              J_{i}^{\star}(\vec{\theta}_{i}(k))&=\underset{\vec{u}_{i}(k:k+N_{p}-1|k)}{\mathrm{minimize}}J_i(k)\\
+              \mathrm{s.t.} &\quad\vec{x}_{i}(k+1)=A_{i}\vec{x}_{i}(k) + B_{i}\vec{u}_{i}(k)\\
+              &\quad\Gamma_{i}\vec{u}_i(k)=\vec{\theta}_{i}(k):\vec{\lambda}_{i}(k)\\
+            \end{aligned}
+          \right\}
+          \small
+          \begin{aligned}
+            &\forall i\in\{1,\dots,M\}\\
+            &\forall j\in\{1,\dots,N_{p}\}
+          \end{aligned}
+          \label{eq:DOP_local}
+          $}
+      \end{equation*}
+      \vfill
+      \begin{equation*}
+        \small
+        \begin{aligned}
+          \only<2>{
+            J^{\star}&=\underset{\vec{\theta}(k:k+N_{p}-1|k)}{\mathrm{minimize}}\sum^{M}_{i=1} J^{\star}_i(\vec{\theta}_i(k))\\
+            \mathrm{s.t.} &\quad \sum_{i=1}^{M}\vec{\theta}_{i}(k)=\vec{u}_{\max}
+          }
+          \only<3->{
+            \vec{\theta}_{i}\pplusone=\vec{\theta}_{i}\p+\rho\left(\vec{\lambda}_{i}^{\star}(\vec{\theta}_{i}\p)-\frac{1}{M}\sum^{M}_{j=1} \vec{\lambda}_{j}^{\star}(\vec{\theta}_{j}\p)\right)
+          }
+        \end{aligned}
+      \end{equation*}
+    \end{minipage}
+  }
+\end{frame}
 % \begin{frame}
@@
 
-\begin{frame}
+\begin{frame}{Quantity Decomposition | Resource Allocation}
   \begin{figure}
     \centering
-    \scalebox{.6}{
+    \scalebox{.55}{
       \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
@@
 
+\begin{frame}{}
+  \centering
+  \vfill
+What if agents send a non-agreed $\vec{\lambda}_{i}$?
+  \vfill
+\end{frame}
+
 \begin{frame}{Outline}
-  \tableofcontents
+  % \tableofcontents
+  \tableofcontents[subsectionstyle=show/show/show]
   % You might wish to add the option [pausesections]
@@
 
-\subsection{The Basic Problem That We Studied}
+\subsection{Attacks}
 
-\begin{frame}{Make Titles Informative. Use Uppercase Letters.}{Subtitles are optional.}
+\begin{frame}{How can a non-cooperative agent attack?}
+
   \begin{itemize}
-  \item
-    Use \texttt{itemize} a lot.
-  \item
-    Use very short sentences or short phrases.
+    \item<1-> $\vec{\lambda}_{i}$ is the only interface with coordination
+    \item<2-> Non-cooperative agent sends $\tilde{\vec{\lambda}}_{i}=\gamma_{i}(\vec{\lambda}_{i})$\pause
   \end{itemize}
+
 \end{frame}
 
-\begin{frame}{Make Titles Informative.}
-  \begin{block}{te}
-
-  \end{block}
-  You can create overlays\dots
+\subsection{Consequences}
+\begin{frame}{Example}
+  \begin{minipage}[c]{.45\linewidth}
+    \begin{figure}[!t]
+      \centering
+      \begin{tikzpicture}
+        \node (0,0){\includegraphics[width=\textwidth]{changeOfJ.pdf}};
+        \draw<4>[rounded corners,red,thick] (-2.5,2.5) rectangle +(.5,-5);
+        \draw<5>[rounded corners,red,thick] (2.5,2.5) rectangle +(.75,-5);
+      \end{tikzpicture}
+    \end{figure}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[c]{.45\linewidth}
+    \begin{exampleblock}{4 distinct agents}
       \begin{itemize}
-  \item using the \texttt{pause} command:
-    \begin{itemize}
-    \item
-      First item.
-      \pause
-    \item
-      Second item.
+        \item<2-> Agent 1 is non-cooperative\\
+        \item<3-> It uses $\tilde{\vec{\lambda}}_{1}=\gamma_{1}(\vec{\lambda}_{1})=\tau_{1}I\vec{\lambda}_{1}$
       \end{itemize}
-  \item
-    using overlay specifications:
-    \begin{itemize}
-    \item<3->
-      First item.
-    \item<4->
-      Second item.
-    \end{itemize}
-  \item
-    using the general \texttt{uncover} command:
-    \begin{itemize}
-      \uncover<5->{\item
-        First item.}
-      \uncover<6->{\item
-        Second item.}
-    \end{itemize}
-  \end{itemize}
+    \end{exampleblock}
+  \end{minipage}
 \end{frame}
-
-\subsection{Previous Work}
 
@@
 \section{Securing the DMPC}
+
+\subsection{Analysis of Subproblems}
+
+\begin{frame}
+  \frametitle{Quadratic Case}
+  \only<1>{
+    \begin{equation*}
+      % \scalebox{.8}{
+      %   $\displaystyle
+          \small
+          \begin{aligned}
+            \underset{\vec{u}_{i}(k:k+N_{p}-1|k)}{\mathrm{minimize}}&\overbrace{\sum_{j=1}^{N_{p}}\|\vec{v}_i(k+j|k)\|^{2}_{Q_i}+\|\vec{u}_i(k+j-1|k)\|^{2}_{R_i}}^{\textstyle J_{i}(k)}\\
+            \mathrm{s.t.} &
+            \left.
+              \begin{aligned}
+                \vec{x}_{i}(\xi+1)=A_{i}\vec{x}_{i}(\xi) + B_{i}\vec{u}_{i}(\xi)\\
+                \Gamma_{i}\vec{u}_i(\xi)=\vec{\theta}_{i}(\xi):\vec{\lambda}_{i}(\xi)\\
+              \end{aligned}
+            \right\}
+            \small
+            \begin{aligned}
+              &\forall \xi\in\{1,\dots,N_{p}\}
+            \end{aligned}
+          \end{aligned}
+          \label{eq:DOP_local}
+        % $}
+    \end{equation*}
+
+  }
+  \only<2->{\begin{equation*}
+    \begin{matrix}
+      \underset{\vec{U}_i(k)}{\mathrm{minimize}}& \overbrace{\frac{1}{2}{\vec{U}_i(k)}^T \alert<3>{H_i}\vec{U}_i(k)+{\alert<4>{\vec{f}_i(k)}}^T\vec{U}_i(k)}^{\textstyle J_{i}(\vec{\theta}_{i})}\\
+      \mathrm{s.t.}&\Theta_{i}\vec{U}_i(k)=\vec{\theta}_{i}:\alert<5>{\vec{\lambda}_{i}}\\
+    \end{matrix}
+  \end{equation*}
+  }
+  \only<6->{
+    \begin{equation*}
+      \vec{\lambda}_{i}=-\alert<7>{P_{i}}\vec{\theta}_{i}-\alert<8>{\vec{s}_{i}(k)}
+    \end{equation*}
+    \centering
+    where ${\alert<7>{P_{i}}={(\Theta_{i}H_{i}^{-1}\Theta_{i}\T)}^{-1}}$ and ${\alert<8>{\vec{s}_{i}(k)}=P_{i}\Theta_{i}H_{i}^{-1}\vec{f}_{i}(k)}$
+  }
+\end{frame}
+
+\subsection{Detection Mechanism}
+\begin{frame}{Detection}
+\begin{assumption}
+  We know nominal $\bar{P}_{i}$
+\end{assumption}
+\pause
+\begin{assumption}
+  Attacker chooses $\tilde{\vec{\lambda}_{i}}=\gamma_{i}(\vec{\lambda}_{i})=T_{i}(k)\vec{\lambda}_{i} $
+  $\to$ $-T_{i}(k)P_{i}\vec{\theta}_{i}-T_{i}(k)\vec{s}_{i}(k)$
+\end{assumption}
+\pause
+\begin{itemize}
+  \item We can estimate%
+        \footnote[1]{Using Recursive Least Squares}
+        $\hat{P}_{i}$ and $\widehat{\tilde{\vec{s}}}_{i}(k)$ such as:
+        \begin{equation*}
+          \label{eq:lambdafuntheta_tilde}
+          \tilde{\vec{\lambda}_{i}}=\gamma_{i}(\vec{\lambda}_{i}(\vec{\theta}_{i}))=-\widehat{\tilde{P}_{i}}(k)\vec{\theta}_{i}-\widehat{\tilde{\vec{s}}}_{i}(k)
+        \end{equation*}
+\pause
+\item If $\widehat{\tilde{{P}}}_{i}(k)\neq\bar{{P}}_{i}$ $\to$ Attack
+\end{itemize}
+\end{frame}
+
+\begin{frame}{About Estimation}
+  \centering
+  \begin{itemize}
+    \item We estimate $\hat{P}_{i}$ and $\widehat{\tilde{\vec{s}}}_{i}(k)$ simultaneously using Recursive Least Squares
+          \pause
+    \item Problem: Estimation during negotiation fails
+          \pause
+          \begin{itemize}
+            \item Consecutive $\vec{\lambda}_{i}^{p}$ and $\vec{\theta}_{i}^{p}$ are linearly dependent $\to$ low input excitation
+          \end{itemize}
+          \pause
+    \item Solution: Send sequence of random values of $\vec{\theta}_{i}$ until estimates converge
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Detection}{In detail}
+  \begin{itemize}
+    \item Error ${E_{i}(k) =\|\widehat{\tilde{P}}_{i}(k)-\bar{P}_{i}\|_{F}}$
+          \pause
+    \item Create threshold $\epsilon_{P}$
+          \pause
+    \item Indicator ${d_{i}\in\{0,1\}}$ detects the attack in agent $i$.
+          \pause
+    \item $d_{i}=1$ if $E_{i}(k)>\epsilon_{P}$, $0$ otherwise
+  \end{itemize}
+\end{frame}
+
+\subsection{Mitigation Mechanism}
+
+\begin{frame}{Mitigation}
+  \begin{itemize}
+    \item Main idea: Reconstruct $\vec{\lambda}_{i}$ and use in negotiation
+  \end{itemize}
+  \pause
+  \begin{assumption}
+    We suppose ${\tilde{\vec{\lambda}}_{i}=\vec{0}}$ only if ${\vec{\lambda}_{i}=\vec{0}}$, which implies $T_{i}(k)$ invertible.
+\end{assumption}\pause
+\begin{itemize}
+  \item Estimate the inverse of $T_{i}(k)$
+        \begin{equation*}
+          {\widehat{T_{i}(k)^{-1}}=\bar{P}_{i}\widehat{\tilde{P}_{i}}(k)^{-1}}
+        \end{equation*}
+        \pause
+  \item Reconstruct $\vec{\lambda}_{i}$
+        \begin{equation*}
+          {\vec{\lambda}_{i}}_{\mathrm{rec}}=\widehat{T_{i}(k)^{-1}} \tilde{\vec{\lambda}_{i}} =-\bar{P}_{i}\vec{\theta}_{i}-\widehat{{T_{i}(k)^{-1}}}\widehat{\tilde{\vec{s}}}_{i}(k)
+        \end{equation*}
+
+\end{itemize}
+\end{frame}
+
+\subsection{Complete Mechanism}
+
+\begin{frame}{Complete Mechanism}
+  \begin{minipage}[c]{.45\linewidth}
+    \begin{figure}[b]
+      \centering
+      \scalebox{.7}{\footnotesize \def\svgwidth{12cm}
+      \input{../img/diagQuantSafe2.pdf_tex}}
+      % \caption{Scheme for Secure DMPC}\label{fig:schemeSafeQuantity}
+    \end{figure}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[c]{.45\linewidth}
+    Two phases:
+    \begin{enumerate}
+      \item Detect which agents are non-cooperative
+      \item Reconstruct $\vec{\lambda}_{i}$ and use in negotiation
+    \end{enumerate}
+  \end{minipage}
+\end{frame}
+
 % \begin{frame}
@@
 
-\begin{frame}
+\begin{frame}{Secure DMPC}
   \begin{figure}[h]
     \centering
-  \scalebox{.6}{
+  \scalebox{.55}{
     \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
@@
 
-\section{Our Results/Contribution}
+\section{Results}
 
-\subsection{Main Results}
-
-\begin{frame}{Make Titles Informative.}
+\begin{frame}{Example}
+  \begin{exampleblock}{Temperature Control of 4 Distinct Rooms Under Power Scarcity}
+    \begin{itemize}
+      \item 4 distinct rooms modeled using 3R-2C
+      \item Initial temperature under $20^{o}\mathrm{C}$
+      \item Not enough power to achieve setpoint $\left({\sum_{i=1}^{4} \vec{u}_{i}(k)\leq4\mathrm{kW}}\right)$
+      \item Simulated for a period of ${5} \mathrm{h}$
+      \item ZOH ${T_{s}=0.25\mathrm{h}}$
+    \end{itemize}
+  \end{exampleblock}
 \end{frame}
 
-\subsection{Basic Ideas for Proofs/Implementation}
-
-\begin{frame}{Make Titles Informative.}
+\begin{frame}{Results}{Temporal}
+  \begin{minipage}[c]{.5\linewidth}
+    \begin{figure}[t]
+      \centering
+      \includegraphics[width=\textwidth]{AirTempAndDecisionVariable.pdf}
+      % \caption{Temperature in room I and the decision variable $E_{I}(k)$}\label{fig:response3Scenarios}
+    \end{figure}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[c]{.45\linewidth}
+    \begin{itemize}
+      \item[N] Nominal
+      \item[S] Selflish behavior
+      \item[C] selfish behavior with Correction
+    \end{itemize}
+  \end{minipage}
 \end{frame}
 
+\begin{frame}
+\frametitle{Results}
+  \begin{table}[t]
+  \centering
+  \caption{Comparison of costs $J_{i}^{N}$ and $J_{G}^{N}$}\label{tab:costsGlobalLocal}
+  \begin{tabular}[t]{cccc} \toprule
+    Agent  & Nominal & Selfish & Selfish + correction\\
+    \midrule
+    I      & 103  &  64  & 104  \\
+    II     &  73  &  91  &  73  \\
+    III    & 100  & 123  & 101  \\
+    IV     & 132  & 154  & 131  \\
+    Global & 408  & 442  & 409  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\end{frame}
 \section*{Summary}
@@
       \item
-            Sub-problems structure has time invariant parameters.
+            Sub-problems' structure has time invariant parameters.
             \pause
-      \item
-            Attacks can be detected using these parameters.
+      \item Attacks can be detected using these parameters.
+            \pause
+      \item Effects can be mitigated.
     \end{enumerate}
@@
 
-  \bibitem{Someone2000}
-    S.~Someone.
-    \newblock On this and that.
-    \newblock {\em Journal of This and That}, 2(1):50--100,
-    2000.
   \end{thebibliography}

### 2021-09-13 presentation/presentation.tex
remove useless slide
notes and webcast options
update sizes
script for presentation

@@
 % \includeonlyframes{current}
+\usepackage{pgfpages}
+% \setbeameroption{show notes on second screen}
+\newif\ifwebcast
+\webcastfalse
+\newcommand{\webcast}{\webcasttrue}
+% \webcast
+\newcommand<>{\script}[1]{\note{\onslide#2{#1}}}
 
@@
   \usefonttheme[onlymath]{serif}
+
 \definecolor{supelecRed}{RGB}{120,30,56}
@@
 \setbeamertemplate{page number in head/foot}[appendixframenumber]
+
 \setbeamertemplate{footline}
@@
 }
-\makeatother
+
+\setbeamertemplate{note page}{
+  \vfill
+\insertnote
+  \vfill
+}
+
+\setbeamersize{text margin right=1.5cm}
+\setbeamersize{text margin left=1.5cm}
 
 \setbeamertemplate{sidebar right}{
+  % \vskip1.3cm%
+  % \llap{\tikz{\draw[fill=black] (.75,0) circle [radius=.75cm]}\hskip0.2cm}%
   \vfill%
@@
   \vskip3pt%
-  \llap{\usebeamertemplate***{navigation symbols}\hskip0.1cm}%
-  \vskip2pt%
-}
+}
+\setbeamertemplate{sidebar left}{
+  \vfill%
+  \ifwebcast{\hspace{3pt}\tikz{\draw[fill=pink,draw=pink] (.6,0) circle [radius=.6cm]}}%
+  \else%
+  % \hspace{3pt}\tikz{\draw[fill=white,draw=white] (.6,0) circle [radius=.6cm]}%
+  \fi
+  \vskip3pt%
+}
+
 \setbeamertemplate{headline}
@@
     \end{beamercolorbox}%
-  % }
     \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,right]{subsection in head/foot}%
@@
 
-\logo{\includegraphics[height=.8cm]{logos/supelec.jpeg}}
+\logo{\includegraphics[width=1.5cm]{logos/supelec.jpeg}}
 
@@
   \titlepage%
+  \note{15 minutes !!!!\\}
+  \script{Hello, I'm Rafael Accácio and on behalf of my co Authors Romain Bourdais and Hervé Guéguen I'm here to present our paper for the SysTol'21 called «Detection and Mitigation of Corrupted Information in Distributed Model Predictive Control Based on Resource Allocation».\\}
+  \script{This presentation is available at the address shown or by flashing the QR code.\\}
 \end{frame}
@@
   \centering
-  Smart City\\
+  % \only<6>{
+  % Smart City\\}
   \begin{minipage}{.45\textwidth}
@@
   \end{minipage}
-  \only<2-5>{
+  \only<1-4>{
   \begin{minipage}{.5\textwidth}
     \begin{itemize}
-      \item<2> Energy Distribution System
-      \item<3> Traffic management
-      \item<4> Heat distribution
-      \item<5> Water distribution
-      \item<5>[] \dots
-    \end{itemize}
-  \end{minipage}
-  }
-\only<6->{
+      \item<+> Energy Distribution System
+      \item<+> Traffic management
+      \item<+> Heat distribution
+      \item<+> Water distribution\\\dots
+    \end{itemize}
+  \end{minipage}
+  }
+\only<5->{
   \begin{minipage}{.5\textwidth}
     \begin{itemize}
-      \item<6> Geographically distributed
-      \item<7> Coupled by constraints (energy)
-      \item<8> Optimization objectives
+      \item<5> Geographically distributed
+      \item<6> Coupled by constraints (energy)
+      \item<7> Optimization objectives
             \begin{itemize}
@@
             \end{itemize}
-      \item<9> Solution $\to$ Model Predictive Control
-    \end{itemize}
-  \end{minipage}
-  }
+      \item<8-> Solution $\to$ Model Predictive Control
+    \end{itemize}
+  \end{minipage}
+  }
+  \script<1->{With the ever increasing connection between systems such as Energy Distribution System, }
+  \script<2->{Traffic management, }
+  \script<3->{Heat distribution, }
+  \script<4->{Water distribution and many others we stroll to the so called smart cities\\}
+  \script<5->{The systems are usually }
+  \script<5->{Geographically distributed }
+  \script<6->{Coupled by constraints as maximum input power or energy }
+  \script<7->{and when they are implemented we try to optimize objectives such as cost, energy, user satisfaction and others.\\ }
+  \script<8>{A solution is to use Model Predictive Control.}
 \end{frame}
@@
   }%
+  \script<1->{The Model based Predictive Control, for those who don't know is a control strategy where the control is computed by solving an optimization problem }
+  \script<2->{with cost J. }
+  \script<3->{The system's response for the input u is predicted for a period Np, }
+  \script<4->{using the model of the system. }
+  \script<5->{And we then add the equality and inequality constraints. }
+  \script<6->{Usually the optimization problem is to minimize a quadratic objective function.}
 \end{frame}
@@
 \begin{frame}{Model Predictive Control}
+  \small
   \only<1->{Find optimal control sequence}%
@@
   \end{figure}
+  \script<1->{We find an optimal control sequence }
+  \script<2->{We apply only the first element }
+  \script<3->{and then we repeat }
 \end{frame}
@@
     \item<1> Problem: Complexity depends on $N_{p},m,p$ and sizes of $\vec{x}$ and $\vec{u}$
-    \item<2> Solution: Divide and Conquer
+    \item<2-> Solution: Divide and Conquer
   \end{itemize}
@@
       }%
-      \only<2>{
+      \only<2->{
         \begin{tikzpicture}[font=\small,thick,node distance=.2cm and .5cm,
@@
   \end{minipage}
+  \script<1->{The problem is when the systems are large, since the complexity depends on Np the number of constraints and sizes of input and states }
+  \script<2->{The solution is to divide the problem where it is separable and use a coordinator to create a consensus in the coupling variables or constraints}
 \end{frame}
@@
   \centering
-  \only<4>{
+  \only<4->{
     \begin{minipage}[t]{.3\linewidth}
@@
   }
+  \script<1->{An example of decomposition method is the Quantity decomposition where a semi-decomposable problem with a global coupling constraints can be decomposed into }
+  \script<2->{multiple sub-problems, which can be solved in parallel, and a master problem which corresponds to the initial problem. \\
+   Those coupling constraints are replaced by local constraints with an allocation theta i. }
+  \script<3->{The allocation for each sub-problem is updated by a projected subgradient method solving the master problem, thus the original problem.
+The subgradient used in this method is the dual variable associated to the coupling constraints}
+  \script<4->{We can represent the sub-problems as agents and the master problem as a coordinator. The coordinator sends the allocations for each agent, which responds with a dual variable. }
 \end{frame}
@@
 \begin{frame}{Quantity Decomposition | Resource Allocation}
+  \centering
+  \begin{minipage}{.45\linewidth}
     \begin{figure}
@@
       }
-    \caption{Quantity decomposition based DMPC}\label{fig:quantityDecompDMPC}
+      % \caption{Quantity decomposition based DMPC}\label{fig:quantityDecompDMPC}
     \end{figure}
+  \end{minipage}
+  \only<7->{\begin{minipage}{.45\linewidth}
+    \begin{figure}
+      \centering
+      \includegraphics[width=\textwidth]{dmpcQuantity4systemsTriche_.mat_thetalambdanegot.pdf}
+    \end{figure}
+  \end{minipage}}
+  \script<1->{In a flowchart for a quantity decomposition based DMPC,}
+  \script<3->{the coordinator sends the allocation theta, }
+  \script<4->{the agents send the dual variable lambda, }
+  \script<5->{the coordinator updates the allocation. }
+  \script<6->{If negotiation converges, }
+  \script<7->{then the negotiation ends and each agent applies the first element of the control found}
 \end{frame}
@@
   \vfill
+  \script<1>{But what if the agents send a non-agreed lambda?}
 \end{frame}
@@
   % \tableofcontents
-  \tableofcontents[subsectionstyle=show/show/show]
+  \tableofcontents[subsectionstyle=show/show/show,pausesections]
   % You might wish to add the option [pausesections]
+  \script<1->{To respond this this presentation is divided into 3 parts.}
+  \script<1->{First We present the vulnerabilites of this decomposition method, }
+  \script<2->{We propose one way to secure the method,}
+  \script<3->{and finally we present our results.}
 \end{frame}
@@
   \end{itemize}
-
+\script<1->{How can an agent attack the system? Its only interface with the coordination is lambda}
+\script<2->{so we suppose it attacks by sending a different $lambda_i$, modified by a function $gamma_i$ of $lambda_i$ }
 \end{frame}
@@
         \node (0,0){\includegraphics[width=\textwidth]{changeOfJ.pdf}};
-        \draw<4>[rounded corners,red,thick] (-2.5,2.5) rectangle +(.5,-5);
-        \draw<5>[rounded corners,red,thick] (2.5,2.5) rectangle +(.75,-5);
+        \draw<4>[rounded corners,red,thick] (-2.3,2.5) rectangle +(.5,-5);
+        \draw<5>[rounded corners,red,thick] (2.3,2.5) rectangle +(.75,-5);
       \end{tikzpicture}
@@
   \end{minipage}
-\end{frame}
-
-\begin{frame}{Make Titles Informative.}
+\script<1->{We give an example of 4 agents negotiating }
+\script<2->{Agent 1 is non-cooperative\\ }
+\script<3->{It uses a linear cheating function gamma tau times identity times the original lambda i\\ }
+\script<3->{In the figure we can see the cost functions for each agent, we see that agent 1 cost decreases if we increase tau, but the overall cost is increased, The minimum value of the global cost is when \\ }
+\script<4->{tau is equal to one. If tau is close to zero it increases its cost and if tau is too high\\ }
+\script<5->{it can turn the negotiation unstable \\ }
 \end{frame}
@@
 \section{Securing the DMPC}
+\script<1->{In order to secure the method let's analyze the subproblems \\ }
 
@@
   }
+\script<1->{If we have a linear system with a quadratic objective function as in the reference tracking problem where we want to minimize the tracking error and the input power\\ }
+\script<2->{we can rewrite as a quadratic program\\ }
+\script<3->{with parameters H\\ }
+\script<4->{and f \\ }
+\script<5->{If we have equality constraints, the dual variables can be calculated explicitly\\ }
+\script<6->{it is an affine function with parameters P and s\\ }
+\script<7->{Observe that P does not depend on the time k\\ }
+\script<8->{meanwhile s does depend, we can use these facts for the detection and mitigation mechanisms\\ }
 \end{frame}
@@
   Attacker chooses $\tilde{\vec{\lambda}_{i}}=\gamma_{i}(\vec{\lambda}_{i})=T_{i}(k)\vec{\lambda}_{i} $
-  $\to$ $-T_{i}(k)P_{i}\vec{\theta}_{i}-T_{i}(k)\vec{s}_{i}(k)$
+
+ \pause $-T_{i}(k)P_{i}\vec{\theta}_{i}-T_{i}(k)\vec{s}_{i}(k)$ $\to$ $-\tilde{P}_{i}\vec{\theta}_{i}-\tilde{\vec{s}_{i}}(k)$
 \end{assumption}
@@
 \end{itemize}
+\script<1->{For the attack detection, let's assume we know the nominal P, called P bar \\ }
+\script<2->{And we also assume the attacker chooses a linear attack where the lambda sent is equal to a matrix T times the original lambda which yields the formula shown \\ }
+\script<3->{with modified P and s, called P tilde and s tilde\\ }
+\script<4->{Now we can estimate P tilde and s tilde for a given negotiation in time k\\ }
+\script<5->{and if the estimated P tilde is different from the nominal P, then there is an attack\\ }
+
 \end{frame}
@@
   \end{itemize}
+\script<1->{In order to estimate the modified P and s, we use recursive least squares\\ }
+\script<2->{The problem of estimating the value during a normal negotiation is that it fails\\ }
+\script<3->{Consecutive lambdas and thetas are linearly dependent, since they are calculate via the projected subgradient method, which gives us low input excitation\\ }
+\script<4->{In order to increase the input excitation we send a sequence of random theta until the convergence is attained\\ }
 \end{frame}
@@
 \begin{frame}{Detection}{In detail}
+  \pause
   \begin{itemize}
@@
   \end{itemize}
+\script<1->{So, let's detail the detection mechanism.\\ }
+\script<2->{First we calculate the norm of the error between the estimated P and the nominal. (Here we use the Frobenius norm)\\ }
+\script<3->{Then, we create a threshold epsilon p\\ }
+\script<4->{and finally we create an indicator d $i$ for the attack of agent $i$\\ }
+\script<5->{It is equal to 1 if the error is greater than the threshold, indicating an attack or 0 otherwise\\ }
 \end{frame}
@@
 \end{itemize}
+\script<1->{Now, for the mitigation the main idea is to reconstruct the original lambda from the estimated parameters and use it in the negotiation\\ }
+\script<2->{We suppose the agent wants to decrease its cost, and the lambda sent is only equal to zero if the original is equal to zero. which implies the matrix T is invertible\\ }
+\script<3->{We can estimate the inverse of T, by using the estimate of P tilde and the nominal value of P like in this equation\\ }
+\script<4->{With the estimate of the inverse of T and the estimate of s tilde, we can reconstruct the original lambda\\ }
 \end{frame}
@@
   \end{minipage}
+  \pause
   \hfill
@@
     Two phases:
+    \pause
     \begin{enumerate}
       \item Detect which agents are non-cooperative
+            \pause
       \item Reconstruct $\vec{\lambda}_{i}$ and use in negotiation
@@
   \end{minipage}
+\script<1->{The complete mechanism is equivalent to add a supervisor for each agent inside the coordinator\\ }
+\script<2->{The mechanism is divided into the two phases, }
+\script<3->{first we detect which agents are non-cooperative }
+\script<4->{and then reconstruct the lambda i s and use in the usual negotiation\\ }
 \end{frame}
@@
 
-      \node[] at (5cm,0cm) {\Large Detection Phase};
-      \node[] at (11cm,0cm) {\Large Negotiation Phase};
+      \node[] at (5cm,0cm) {\Large \alert<2>{Detection Phase}};
+      \node[] at (11cm,0cm) {\Large \alert<3>{Negotiation Phase}};
 
@@
       fill=gray!90!black!50,
-      alt=<{2}>{fill=supelecRed!90,text=white},
+      alt=<{4}>{fill=supelecRed!90,text=white},
       minimum width=2.5cm,
@@
       fill=supelecRed!10,
-      alt=<{3}>{fill=supelecRed!90,text=white},
+      alt=<{5}>{fill=supelecRed!90,text=white},
       below=of block1,
@@
       fill=supelecRed!10,
-      alt=<{4}>{fill=supelecRed!90,text=white},
+      alt=<{6}>{fill=supelecRed!90,text=white},
       below=of block2,
@@
       fill=supelecRed!10,
-      alt=<{5}>{fill=supelecRed!90,text=white},
+      alt=<{7}>{fill=supelecRed!90,text=white},
       minimum width=3.5cm,
@@
       fill=supelecRed!50,
-      alt=<{6}>{fill=supelecRed!90,text=white},
+      alt=<{8}>{fill=supelecRed!90,text=white},
       align=center,
@@
       fill=supelecRed!10,
-      alt=<{7}>{fill=supelecRed!90,text=white},
+      alt=<{9}>{fill=supelecRed!90,text=white},
       right=1cm of block5,
@@
       fill=supelecRed!10,
-      alt=<{8}>{fill=supelecRed!90,text=white},
+      alt=<{10}>{fill=supelecRed!90,text=white},
       minimum width=3.5cm,
@@
       fill=supelecRed!10,
-      alt=<{9}>{fill=supelecRed!90,text=white},
+      alt=<{11}>{fill=supelecRed!90,text=white},
       below=of block7,
@@
       fill=supelecRed!10,
-      alt=<{10}>{fill=supelecRed!90,text=white},
+      alt=<{12}>{fill=supelecRed!90,text=white},
       below=of block8,
@@
       fill=supelecRed!50,
-      alt=<{11}>{fill=supelecRed!90,text=white},
+      alt=<{13}>{fill=supelecRed!90,text=white},
       align=center,
@@
       fill=gray!90!black!50,
-      alt=<{12}>{fill=supelecRed!90,text=white},
+      alt=<{14}>{fill=supelecRed!90,text=white},
       minimum width=2.5cm,
@@
     }
-    \caption{Secure DMPC}\label{fig:secureDMPC}
+    % \caption{Secure DMPC}\label{fig:secureDMPC}
   \end{figure}
+  \script<1->{Now, for the complete secure DMPC algorithm, as said it is divided into two phases\\ }
+  \script<2->{The Detection phase \\ }
+  \script<3->{and the negotiation phase\\ }
+  \script<5->{The coordinator sends random theta i\\ }
+  \script<6->{The agents send dual variable lambda i\\ }
+  \script<7->{The coordinator estimates the parameters P and s tilde\\ }
+  \script<8->{when the estimates converge\\ }
+  \script<9->{The coordinator detects which agents are non-cooperative\\ }
+  \script<10->{then the negotiation phase begins, the coordinator sends the theta i\\ }
+  \script<11->{the agents send the dual variable lambda i\\ }
+  \script<12->{and the coordinator updates the allocation accordingly using the reconstructed lambda or the one sent by the agent\\ }
+  \script<13->{and once the negotiation converges\\ }
+  \script<14->{each agent applies the first control\\ }
+
 \end{frame}
@@
 \section{Results}
-
+\script{Now, for some results}
 \begin{frame}{Example}
@@
     \begin{itemize}
+            \pause
       \item 4 distinct rooms modeled using 3R-2C
+            \pause
       \item Initial temperature under $20^{o}\mathrm{C}$
+            \pause
       \item Not enough power to achieve setpoint $\left({\sum_{i=1}^{4} \vec{u}_{i}(k)\leq4\mathrm{kW}}\right)$
+            \pause
       \item Simulated for a period of ${5} \mathrm{h}$
+            \pause
       \item ZOH ${T_{s}=0.25\mathrm{h}}$
+            \pause
+      \item 3 scenarios
+            \begin{enumerate}
+              \item Nominal
+              \item Agent I non cooperative from k>6 with T=4*I
+              \item Similar but with secure algorithm
+            \end{enumerate}
     \end{itemize}
   \end{exampleblock}
+  \script<1->{We give an academic example of the temperature control of 4 distinct rooms under power scarcity\\}
+  \script<2->{The 4 rooms are distinct using the 3 resistor 2 capacitor model\\}
+  \script<3->{the initial temperature of all rooms is under 20 degrees celsius, which is the final setpoint\\}
+  \script<4->{But they are under power scarcity that prevents them from reaching the setpoint\\}
+  \script<5->{we simulate for a period of 5h\\}
+  \script<6->{with sampling time of 15 minutes\\}
+  \script<7->{3 scenarios are simulated, the nominal, one where agent 1 presents non cooperative behavior from k greater than 6, and another with the selfish behavior and the secure mechanism activated\\}
 \end{frame}
@@
       \item[C] selfish behavior with Correction
-    \end{itemize}
-  \end{minipage}
+    \end{itemize}\pause
+  \end{minipage}
+  \script<1->{In the figure we see the air temperature and the estimation error for room 1\\}
+  \script<2->{The nominal behavior is in orange, and as said it cannot reach the setpoint, in blue\\}
+  \script<3->{When the room presents selfish behavior (in blue), it reduces its cost and get closer to the setpoint, we see that the attack increases the error\\}
+  \script<4->{Now, for the case with correction (the red dots), even if it attacks the system, the temperature is close to its nominal value\\}
 \end{frame}
@@
   \end{tabular}
+  \pause
+  \script<1->{Now, if we compare the costs for each scenario we see how the cost of agent 1 decreases when it attacks, while the cost of other agents increase.\\}
+  \script<2->{When the secure algorithm is activated the costs are very close to the original ones. So }
 \end{table}
@@
   \end{minipage}
+  \script<1->{We can see that\\}
+  \script<2->{Resource allocation based DMPC is vulnerable to attacks.\\}
+  \script<3->{Sub-problems' structure has time invariant parameters.\\}
+  \script<4->{Attacks can be detected using these parameters.\\}
+  \script<5->{and Effects can be mitigated.\\}
+  \script<6->{An outlook for future works \\}
+  \script<7->{is to use inequality constraints instead of only equality constraints, which will yield hybrid behavior\\}
+  \script<8->{and try to implement with non-linear attack models\\}
+
 \end{frame}
@@
   \end{thebibliography}
+    \script{As a recommended reading I give a book about distributed MPC and an article with another secure dmpc algorithm based in another decomposition method. That's all\\}
+
 \end{frame}
@@
   \vfill
-  Questions?
+  Thank you!
   \vfill
@@
   \end{minipage}
+  \ifwebcast{\tikz{\draw[fill=pink,draw=pink] (1.5,0) circle [radius=1.5cm]}}%
+  \fi
+      \script{If you want to see the simulations of this paper we have a github repository, and if you want to send me an email about this paper or this presentation you can flash the QR code in the right.
+Thank you!\\}
+
 \end{frame}

### 2021-09-13 presentation/presentation.tex
update paper presentation

@@
   \note{15 minutes !!!!\\}
-  \script{Hello, I'm Rafael Accácio and on behalf of my co Authors Romain Bourdais and Hervé Guéguen I'm here to present our paper for the SysTol'21 called «Detection and Mitigation of Corrupted Information in Distributed Model Predictive Control Based on Resource Allocation».\\}
+  \script{Hello, I'm Rafael Accácio and on behalf of my colleagues Romain Bourdais and Hervé Guéguen I'm here to present our paper for the SysTol'21 called «Detection and Mitigation of Corrupted Information in Distributed Model Predictive Control Based on Resource Allocation».\\}
   \script{This presentation is available at the address shown or by flashing the QR code.\\}

### 2021-09-13 script/decompositionNagents.m
add matlab scripts

@@ -1,0 +1,103 @@
+% [[file:../../../docs/org/decomposition_methods/secureDMPC.org::*Define simulation parameters][Define simulation parameters:1]]
+clear
+addpath("aux")
+paren = @(x, varargin) x(varargin{:}); %
+                                       % apply index in created elements
+curly = @(x, varargin) x{varargin{:}}; %
+
+options = optimset('Display', 'off')
+
+chSetpoint = 0;
+cheating = 0;
+secure = 0;
+% Define simulation parameters:1 ends here
+
+% [[file:../../../docs/org/decomposition_methods/secureDMPC.org::*Define simulation parameters][Define simulation parameters:2]]
+% simK = 40;
+simK = 20;
+negotP = 200;
+% Define simulation parameters:2 ends here
+
+% [[file:../../../docs/org/decomposition_methods/secureDMPC.org::*Define simulation parameters][Define simulation parameters:3]]
+proj=@(x,A,b) x-A/(A'*A)*(A'*x-b);
+% Define simulation parameters:3 ends here
+
+% [[file:../../../docs/org/decomposition_methods/secureDMPC.org::*Define the systems and coordinator][Define the systems and coordinator:1]]
+Nsystems
+% Define the systems and coordinator:1 ends here
+
+% [[file:../../../docs/org/decomposition_methods/secureDMPC.org::*Define the systems and coordinator][Define the systems and coordinator:13]]
+Ac=kron(ones(1,M),eye(n))' ; %
+                             % Global Constraints
+bc = Umax*ones(1,n)' ;       %
+% Define the systems and coordinator:13 ends here
+
+% [[file:../../../docs/org/decomposition_methods/secureDMPC.org::*Define the systems and coordinator][Define the systems and coordinator:14]]
+if cheating
+  subsystems=getSubsystems(sys,Q,R,n,@applyCheat); % cheating using profile
+else
+  subsystems=getSubsystems(sys,Q,R,n); %no cheating
+end
+clear Q R
+% Define the systems and coordinator:14 ends here
+
+% [[file:../../../docs/org/decomposition_methods/secureDMPC.org::*Define the systems and coordinator][Define the systems and coordinator:15]]
+if secure
+%   coordinator=getCoordinator(@onlineSecure); % online secure method using RLS
[…]

### 2021-09-13 script/getLambdas.m

@@ -1,0 +1,24 @@
+% [[file:../../../docs/org/decomposition_methods/secureDMPC.org::*getLambdas][getLambdas:1]]
+function [subsystems, lambdas ] = getLambdas(subsystems,theta,negot,K)
+    options=evalin('base','options');
+
+    % here we suppose the setpoint won't change in the future
+    for i=1:subsystems.M
+        newWt(:,:,i)=kron(subsystems.Wt(:,K,i),ones(1,subsystems.n));
+        F(:,:,i)=subsystems.getF(subsystems.Cmat(:,:,i), subsystems.Mmat(:,:,i), subsystems.Q(:,:,i), subsystems.xt(:,K,i), newWt(:,:,i)');
+        const(:,:,i)= subsystems.getc(subsystems.Mmat(:,:,i), subsystems.Q(:,:,i),subsystems.xt(:,K,i),newWt(:,:,i)');
+        % [u1(:,negot,K),J1(1,negot,K),c1,~,lambda1new] = quadprog(H(:,:,1), F(:, :,1), [], [], eye(n*c), theta(:,1)', umin*ones(size(Bd1,2)*n,1), umax*ones(size(Bd1,2)*n,1), [], options);
+
+        %[x,fval,exitflag,output,lambda] = quadprog(H, f, A, b, Aeq, beq, lb, ub, x0, options)
+
+        [u(:,i),J(:,i),~,~,l] = quadprog(subsystems.H(:,:,i), F(:,:,i), [], [], eye(subsystems.n*subsystems.c), theta(:,i)', subsystems.umin(:,i)*ones(subsystems.c*subsystems.n,1), subsystems.umax(:,i)*ones(subsystems.c*subsystems.n,1), [], options);
+
+
+        lambdas(:,i)=l.eqlin;
+    end
+    subsystems.u(:,:)=u;
+    subsystems.uHist(:,negot,K,:)=u;
+    subsystems.J(:,K,:)=J;
+    lambdas = subsystems.applyCheat(lambdas,K);
+end
+% getLambdas:1 ends here

### 2022-07-21 article/article.tex
prevent compiling
move img folder
update copyright warning
correct error
use norm function
use RR
change copyright

@@
+\loop\iftrue%
+\errmessage{This article is copyrighted by IEEE and should not be TeXed}%
+\repeat%
+
 \documentclass[a4paper, 10 pt, conference]{ieeeconf}  % Comment this line out
@@
 \pubid{\begin{minipage}{\textwidth}\ \\[50pt]\centering
-  \copyright 2021 IEEE. Personal use is permitted, but republication/redistribution requires IEEE permission.\\
-See https://www.ieee.org/publications/rights/index.html for more information.
+    \copyright{} 2021 IEEE.
+Personal use of this material is permitted.
+Permission from IEEE must be obtained for all other uses, in any current or future media, including reprinting/republishing this material for advertising or promotional purposes, creating new collective works, for resale or redistribution to servers or lists, or reuse of any copyrighted component of this work in other works.
+% copyright notice in https://journals.ieeeauthorcenter.ieee.org/become-an-ieee-journal-author/publishing-ethics/guidelines-and-policies/post-publication-policies
 \end{minipage}}
 % \makeglossaries
-\markboth{Oi}{test}
 \begin{document}
@@
 \section{PRELIMINARIES AND PROBLEM STATEMENT}\label{sec:PS}
-\emph{Notation:} In this paper, $\|\cdot\|$ and $\|\cdot\|_{F}$ represent the $\ell_{2}$ and Frobenius norms. $\|\vec{v}\|_{Y}$ is the weighted norm, $\|Y^{\frac{1}{2}}\vec{v}\|$.
+\emph{Notation:} In this paper, $\norm{\cdot}$ and $\norm{\cdot}_{F}$ represent the $\ell_{2}$ and Frobenius norms. $\norm{\vec{v}}_{Y}$ is the weighted norm, $\norm{Y^{\frac{1}{2}}\vec{v}}$.
 $P_{\mathsf{T}}(\cdot)$ is the Euclidean projection onto set $\mathsf{T}$.
@@
 \end{equation}
-where $\Gamma_{i}:\R^{\pi_{\vec{u}_{i}(k)}\times \pi_{\vec{u}_{i}(k)}}$ and $\vec{u}_{\mathrm{max}}:\R^{\pi_{\vec{u}_{i}(k)}\times 1}$.
+where $\Gamma_{i}:\RR^{\pi_{\vec{u}_{i}(k)}\times \pi_{\vec{u}_{i}(k)}}$ and $\vec{u}_{\mathrm{\max}}:\RR^{\pi_{\vec{u}_{i}(k)}\times 1}$.
 
@@
   \centering
- \footnotesize \def\svgwidth{0.44\textwidth} \input{./img/diagQuantMod.pdf_tex}
+ \footnotesize \def\svgwidth{0.44\textwidth} \input{../img/diagQuantMod.pdf_tex}
  \caption{Scheme of DMPC using a \emph{coordinator} and $M$ agents.}\label{fig:schemeQuantity}
@@
   \scriptsize \def\svgwidth{0.49\textwidth}
-\input{img/diagQuantSafe2.pdf_tex}
+\input{../img/diagQuantSafe2.pdf_tex}
   \caption{Scheme for Secure DMPC}\label{fig:schemeSafeQuantity}
